---
title: "Data Exploration"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)
```

# Load packages
```{r load-packages, message=FALSE}
library(tidyverse)
library(ggplot2)
library(shiny)
library(infer)
library(data.table)
```

# Load data
```{r load-data}
pre_empower <- read.csv("data/PRE_Empowerment.csv",
                    sep = ";")
post_empower <- read.csv("data/POST_Empowerment.csv",
                    sep = ";")
pre_2019 <- read.csv("data/PRE2019.csv",
                    sep = ";")
post_2019 <- read.csv("data/POST2019.csv",
                    sep = ";")
```

## Include columns that indicate whether responses are from pre- or post-implementation surveys, and what year they were collected
```{r data}
pre_empower <- pre_empower %>%
  mutate(pre_or_post = "Pre") %>%
  mutate(year = "2018")
post_empower <- post_empower %>%
  mutate(pre_or_post = "Post") %>%
  mutate(year = "2018")
pre_2019 <- pre_2019 %>%
  mutate(pre_or_post = "Pre") %>%
  mutate(year = "2019")
post_2019 <- post_2019 %>%
  mutate(pre_or_post = "Post") %>%
  mutate(year = "2019")
```

## Count how many students took the pre- and post-implementation surveys in 2018 and 2019
```{r}
count(pre_empower)
count(post_empower)
count(pre_2019)
count(post_2019)
```

```{r}
pre_empower %>%
  group_by(grade) %>%
  count
post_empower %>%
  group_by(grade) %>%
  count
pre_2019 %>%
  group_by(grade) %>%
  count
post_2019 %>%
  group_by(grade) %>%
  count
```


## Join pre- and post-implementation data into one dataset. Then join data from 2018 and 2019 into one dataset
```{r}
empower_2018 <- full_join(pre_empower, post_empower) %>%
  select(-c(other_plan_afterschool))
empower_2019 <- full_join(pre_2019, post_2019) %>%
  select(-c(other_plan_afterschool))
empower_2019$grade <- as.factor(empower_2019$grade)
empower <- full_join(empower_2018, empower_2019)
```

## Rename to positive vs. negative feelings from A, B, C, D, E (as they were on the survey) to 1, 2, 3, 4, 5
```{r change-names}
change_names <- function(naming){
naming %>%
  str_replace("A", "1") %>%
  str_replace("B", "2") %>%
  str_replace("C", "3") %>%
  str_replace("D", "4") %>%
  str_replace("E", "5")
}

empower$math_worst <- change_names(empower$math_worst)
empower$math_career <- change_names(empower$math_career)
empower$not_enjoy_math <- change_names(empower$not_enjoy_math)
empower$good_at_math <- change_names(empower$good_at_math)
empower$decentschool_badmath <- change_names(empower$decentschool_badmath)
empower$higherlevel_math <- change_names(empower$higherlevel_math)
empower$good_math_grades <- change_names(empower$good_math_grades)
empower$interesting_math <- change_names(empower$interesting_math)
empower$future_math <- change_names(empower$future_math)
empower$math_courses <- change_names(empower$math_courses)
empower$sure_science <- change_names(empower$sure_science)
empower$science_career <- change_names(empower$science_career)
empower$science_outsideofschool <- change_names(empower$science_outsideofschool)
empower$science_pay <- change_names(empower$science_pay)
empower$science_job <- change_names(empower$science_job)
empower$good_science <- change_names(empower$good_science)
empower$decentschool_badscience <- change_names(empower$decentschool_badscience)
empower$higherlevel_science <- change_names(empower$higherlevel_science)
empower$science_courses <- change_names(empower$science_courses)
empower$new_products <- change_names(empower$new_products)
empower$engineering_everyday <- change_names(empower$engineering_everyday)
empower$enjoy_building <- change_names(empower$enjoy_building)
empower$interested_machines <- change_names(empower$interested_machines)
empower$career_design <- change_names(empower$career_design)
empower$curiosity_tech <- change_names(empower$curiosity_tech)
empower$future_innovation <- change_names(empower$future_innovation)
empower$mathscience_useful <- change_names(empower$mathscience_useful)
empower$success_engineering <- change_names(empower$success_engineering)
empower$i_can_build <- change_names(empower$i_can_build)
empower$opportunity_engineering <- change_names(empower$opportunity_engineering)
empower$contribute_community <- change_names(empower$contribute_community)
empower$resolve_problems_community <- change_names(empower$resolve_problems_community)
empower$external_help <- change_names(empower$external_help)
empower$leader_community <- change_names(empower$leader_community)
empower$contribute_community.1 <- change_names(empower$contribute_community.1)
```

## Create different datasets for each question that will be analyzed. Each dataset should have the variables: "pre_or_post", "all" (the response - whether students feel positively or negatively towards the question), "grade" (the respondent's grade level), and "class" (which classifies which course the question refers to - EGR, math, or science)

### EGR
```{r}
new_products <- empower %>%
  select(pre_or_post, new_products, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "new_products")
names(new_products) <- c("pre_or_post", "all", "grade", "class", "question")

engineering_everyday <- empower %>%
  select(pre_or_post, engineering_everyday, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "engineering_everyday")
names(engineering_everyday) <- c("pre_or_post", "all", "grade", "class", "question")

enjoy_building <- empower %>%
  select(pre_or_post, enjoy_building, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "enjoy_building")
names(enjoy_building) <- c("pre_or_post", "all", "grade", "class", "question")

interested_machines <- empower %>%
  select(pre_or_post, interested_machines, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "interested_machines")
names(interested_machines) <- c("pre_or_post", "all", "grade", "class", "question")

career_design <- empower %>%
  select(pre_or_post, career_design, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "career_design")
names(career_design) <- c("pre_or_post", "all", "grade", "class", "question")

curiosity_tech <- empower %>%
  select(pre_or_post, curiosity_tech, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "curiosity_tech")
names(curiosity_tech) <- c("pre_or_post", "all", "grade", "class", "question")

future_innovation <- empower %>%
  select(pre_or_post, future_innovation, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "future_innovation")
names(future_innovation) <- c("pre_or_post", "all", "grade", "class", "question")

mathscience_useful <- empower %>%
  select(pre_or_post, mathscience_useful, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "mathscience_useful")
names(mathscience_useful) <- c("pre_or_post", "all", "grade", "class", "question")

success_engineering <- empower %>%
  select(pre_or_post, success_engineering, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "success_engineering")
names(success_engineering) <- c("pre_or_post", "all", "grade", "class", "question")

i_can_build <- empower %>%
  select(pre_or_post, i_can_build, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "i_can_build")
names(i_can_build) <- c("pre_or_post", "all", "grade", "class", "question")

opportunity_engineering <- empower %>%
  select(pre_or_post, opportunity_engineering, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "opportunity")
names(opportunity_engineering) <- c("pre_or_post", "all", "grade", "class", "question")
```

### Science
```{r}
sure_science <- empower %>%
  select(pre_or_post, sure_science, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "sure_science")
names(sure_science) <- c("pre_or_post", "all", "grade", "class", "question")

science_career <- empower %>%
  select(pre_or_post, science_career, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_career")
names(science_career) <- c("pre_or_post", "all", "grade", "class", "question")

science_outsideofschool <- empower %>%
  select(pre_or_post, science_outsideofschool, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_outsideofschool")
names(science_outsideofschool) <- c("pre_or_post", "all", "grade", "class", "question")

science_pay <- empower %>%
  select(pre_or_post, science_pay, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_pay")
names(science_pay) <- c("pre_or_post", "all", "grade", "class", "question")

science_job <- empower %>%
  select(pre_or_post, science_job, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_job")
names(science_job) <- c("pre_or_post", "all", "grade", "class", "question")

good_science <- empower %>%
  select(pre_or_post, good_science, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "good_science")
names(good_science) <- c("pre_or_post", "all", "grade", "class", "question")

higherlevel_science <- empower %>%
  select(pre_or_post, higherlevel_science, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "higherlevel_science")
names(higherlevel_science) <- c("pre_or_post", "all", "grade", "class", "question")

science_courses <- empower %>%
  select(pre_or_post, science_courses, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_courses")
names(science_courses) <- c("pre_or_post", "all", "grade", "class", "question")

decentschool_badscience <- empower %>%
  select(pre_or_post, decentschool_badscience, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "decentschool_badscience")
names(decentschool_badscience) <- c("pre_or_post", "all", "grade", "class", "question")
```


### Math
```{r}
math_career <- empower %>%
  select(pre_or_post, math_career, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "math_career")
names(math_career) <- c("pre_or_post", "all", "grade", "class", "question")

good_at_math <- empower %>%
  select(pre_or_post, good_at_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "good_at_math")
names(good_at_math) <- c("pre_or_post", "all", "grade", "class", "question")

higherlevel_math <- empower %>%
  select(pre_or_post, higherlevel_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "higherlevel_math")
names(higherlevel_math) <- c("pre_or_post", "all", "grade", "class", "question")

good_math_grades <- empower %>%
  select(pre_or_post, good_math_grades, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "good_math_grades")
names(good_math_grades) <- c("pre_or_post", "all", "grade", "class", "question")

interesting_math <- empower %>%
  select(pre_or_post, interesting_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "interesting_math")
names(interesting_math) <- c("pre_or_post", "all", "grade", "class", "question")

future_math <- empower %>%
  select(pre_or_post, future_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "future_math")
names(future_math) <- c("pre_or_post", "all", "grade", "class", "question")

math_courses <- empower %>%
  select(pre_or_post, math_courses, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "math_courses")
names(math_courses) <- c("pre_or_post", "all", "grade", "class", "question")

math_worst <- empower %>%
  select(pre_or_post, math_worst, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "math_worst")
names(math_worst) <- c("pre_or_post", "all", "grade", "class", "question")

not_enjoy_math <- empower %>%
  select(pre_or_post, not_enjoy_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "not_enjoy_math")
names(not_enjoy_math) <- c("pre_or_post", "all", "grade", "class", "question")

decentschool_badmath <- empower %>%
  select(pre_or_post, decentschool_badmath, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "decentschool_badmath")
names(decentschool_badmath) <- c("pre_or_post", "all", "grade", "class", "question")
```

### Helping community

```{r}
contribute_community <- empower %>%
  select(pre_or_post, contribute_community, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "contribute_community")
names(contribute_community) <- c("pre_or_post", "all", "grade", "class", "question")

resolve_problems_community <- empower %>%
  select(pre_or_post, resolve_problems_community, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "resolve_problems_community")
names(resolve_problems_community) <- c("pre_or_post", "all", "grade", "class", "question")

external_help <- empower %>%
  select(pre_or_post, external_help, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "external_help")
names(external_help) <- c("pre_or_post", "all", "grade", "class", "question")

leader_community <- empower %>%
  select(pre_or_post, leader_community, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "leader_community")
names(leader_community) <- c("pre_or_post", "all", "grade", "class", "question")

contribute_community.1 <- empower %>%
  select(pre_or_post, contribute_community.1, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "contribute_community.1")
names(contribute_community.1) <- c("pre_or_post", "all", "grade", "class", "question")
```


```{r}
together <- rbind(new_products,
             engineering_everyday,
             enjoy_building,
             interested_machines,
             career_design,
             curiosity_tech,
             future_innovation,
             mathscience_useful,
             success_engineering,
             i_can_build,
             opportunity_engineering, 
             sure_science,
             science_career, 
             science_outsideofschool,
             science_pay,
             science_job,
             good_science,
             higherlevel_science,
             science_courses,
             math_career,
             good_at_math,
             higherlevel_math,
             good_math_grades,
             interesting_math,
             future_math,
             math_courses)
```

```{r}
others <- rbind(math_worst, 
                not_enjoy_math,
                decentschool_badmath,
                decentschool_badscience,
                contribute_community,
                resolve_problems_community,
                external_help,
                leader_community,
                contribute_community.1)
```


```{r}
together$grade <- together$grade %>%
  str_replace("5 bach", "5") %>%
  str_replace("5 mag", "5")
together <- transform(together, all = as.numeric(all))
```

```{r}
together %>%
  filter(!is.na(all)) %>%
  group_by(pre_or_post) %>%
  count(question)
```

```{r}
observations1 <- together %>%
  group_by(question, pre_or_post, grade) %>%
  filter(!is.na(all)) %>%
  count()
observations1
```

```{r}
others$grade <- others$grade %>%
  str_replace("5 bach", "5") %>%
  str_replace("5 mag", "5")
others <- transform(others, all = as.numeric(all))
```

```{r}
observations2 <- others %>%
  group_by(question, pre_or_post, grade) %>%
  filter(!is.na(all)) %>%
  count()
observations2
```

```{r}
first_others <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
first_others
```

```{r}
second_others <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
second_others
```

```{r}
third_others <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
third_others
```

```{r}
set.seed(2019)
perm_third_others <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_third_others %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
fifth_others <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
fifth_others
```

```{r}
set.seed(2019)
perm_fifth_others <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_fifth_others %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


# MATH

### Math career 
2. I consider choosing a career related to mathematics.

YES
```{r}
grade1_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "math_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_math_career
```

```{r}
set.seed(2019)
perm_grade1_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "math_career") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_math_career %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


```{r}
grade2_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "math_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_math_career
```

YES
```{r}
grade3_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "math_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_math_career
```

```{r}
set.seed(2019)
perm_grade3_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "math_career") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_math_career %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "math_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_math_career
```

```{r}
set.seed(2019)
perm_grade5_math_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "math_career") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_math_career %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Good at math
4. I'm the kind of student who usually does well in math.

```{r}
grade1_good_at_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "good_at_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_good_at_math
```

```{r}
grade2_good_at_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "good_at_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_good_at_math
```

YES
```{r}
grade3_good_at_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "good_at_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_good_at_math
```

```{r}
set.seed(2019)
perm_grade3_good_at_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "good_at_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_good_at_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_good_at_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "good_at_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_good_at_math
```

```{r}
set.seed(2019)
perm_grade5_good_at_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "good_at_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_good_at_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Higher level math
6. I consider taking higher level math courses.

```{r}
grade1_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "higherlevel_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_higherlevel_math
```

YES
```{r}
grade2_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "higherlevel_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_higherlevel_math
```

```{r}
set.seed(2019)
perm_grade2_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "higherlevel_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_higherlevel_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "higherlevel_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_higherlevel_math
```

```{r}
set.seed(2019)
perm_grade3_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "higherlevel_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_higherlevel_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "higherlevel_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_higherlevel_math
```

```{r}
set.seed(2019)
perm_grade5_higherlevel_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "higherlevel_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_higherlevel_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


### Good math grades
7. I got good grades in math

YES
```{r}
grade1_good_math_grades <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "good_math_grades") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_good_math_grades
```

```{r}
set.seed(2019)
perm_grade1_good_math_grades <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "good_math_grades") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_good_math_grades %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade2_good_math_grades <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "good_math_grades") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_good_math_grades
```

```{r}
grade3_good_math_grades <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "good_math_grades") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_good_math_grades
```

YES
```{r}
grade5_good_math_grades <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "good_math_grades") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_good_math_grades
```

```{r}
set.seed(2019)
perm_grade5_good_math_grades <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "good_math_grades") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_good_math_grades %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Interesting math
8. I think mathematics is interesting

```{r}
grade1_interesting_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "interesting_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_interesting_math
```

```{r}
grade2_interesting_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "interesting_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_interesting_math
```

```{r}
grade3_interesting_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "interesting_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_interesting_math
```

YES
```{r}
grade5_interesting_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "interesting_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_interesting_math
```

```{r}
set.seed(2019)
perm_grade5_interesting_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "interesting_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_interesting_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Future Math
9. I plan to use mathematics in my future career.

```{r}
grade1_future_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "future_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all))
grade1_future_math
```

```{r}
grade2_future_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "future_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_future_math
```

YES
```{r}
grade3_future_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "future_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_future_math
```

```{r}
set.seed(2019)
perm_grade3_future_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "future_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_future_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_future_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "future_math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all))
grade5_future_math
```

```{r}
grade5_future_math$pre_or_post <- factor(grade5_future_math$pre_or_post, levels = c("Pre", "Post"))

tiff("mathematics_future_career.tiff", units="in", width=7, height=9, res=300)
ggplot(data = grade5_future_math, mapping = aes(x = pre_or_post, y = mean)) +
  geom_bar(stat = "identity", fill = "slategray4") +
    labs(title = "I plan to use mathematics in my future career", subtitle = "11th graders", x = "", y = "Average Positivity Towards STEM") +
  theme(plot.title = element_text(size = 22),
  plot.subtitle = element_text(size = 18),
  axis.text=element_text(size=16),
  axis.title=element_text(size=20),
  legend.title=element_text(size=18),
  legend.text=element_text(size=16),
  strip.text=element_text(size=14),
  legend.position ="none")
dev.off()
```

```{r}
set.seed(2019)
perm_grade5_future_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "future_math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_future_math %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Math courses
10. I would like the opportunity to take more math courses.

```{r}
grade1_math_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "math_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_math_courses
```

YES
```{r}
grade2_math_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "math_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_math_courses
```

```{r}
set.seed(2019)
perm_grade2_math_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "math_courses") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_math_courses %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade3_math_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "math_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_math_courses
```

YES
```{r}
grade5_math_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "math_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_math_courses
```

```{r}
set.seed(2019)
perm_grade5_math_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "math_courses") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_math_courses %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


# SCIENCE

### Sure science
11. I feel safe in science classes.

```{r}
grade1_sure_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "sure_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_sure_science
```

```{r}
grade2_sure_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "sure_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_sure_science
```

```{r}
grade3_sure_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "sure_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_sure_science
```

YES
```{r}
grade5_sure_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "sure_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_sure_science
```

```{r}
set.seed(2019)
perm_grade5_sure_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "sure_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_sure_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


### Science career
12. I consider a career related to science.

```{r}
grade1_science_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "science_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_science_career
```

```{r}
grade2_science_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_science_career
```

YES
```{r}
grade3_science_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_science_career
```

```{r}
set.seed(2019)
perm_grade3_science_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_career") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_science_career %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_science_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_career") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_science_career
```

```{r}
set.seed(2019)
perm_grade5_science_career <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_career") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_science_career %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Science outside of school
13. I think I will use science when I leave school.

```{r}
grade1_science_outsideofschool <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "science_outsideofschool") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_science_outsideofschool
```

YES
```{r}
grade2_science_outsideofschool <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_outsideofschool") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_science_outsideofschool
```

```{r}
set.seed(2019)
perm_grade2_science_outsideofschool <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_outsideofschool") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_science_outsideofschool %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade3_science_outsideofschool <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_outsideofschool") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_science_outsideofschool
```

YES
```{r}
grade5_science_outsideofschool <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_outsideofschool") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_science_outsideofschool
```

```{r}
set.seed(2019)
perm_grade5_science_outsideofschool <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_outsideofschool") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_science_outsideofschool %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Science pay
14. Knowledge of science will help me earn a living.

YES
```{r}
grade1_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "science_pay") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_science_pay
```

```{r}
set.seed(2019)
perm_grade1_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "science_pay") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_science_pay %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_pay") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_science_pay
```

```{r}
set.seed(2019)
perm_grade2_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_pay") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_science_pay %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_pay") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_science_pay
```

```{r}
set.seed(2019)
perm_grade3_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_pay") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_science_pay %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade5_science_pay <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_pay") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_science_pay
```

### Science job
15. I need science for my future work.

```{r}
grade1_science_job <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "science_job") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_science_job
```

```{r}
grade2_science_job <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_job") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_science_job
```

YES
```{r}
grade3_science_job <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_job") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_science_job
```

```{r}
set.seed(2019)
perm_grade3_science_job <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_job") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_science_job %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade5_science_job <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_job") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_science_job
```

### Good science
16. I know I can do well in science classes

```{r}
grade1_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "good_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_good_science
```

YES
```{r}
grade2_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "good_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_good_science
```

```{r}
set.seed(2019)
perm_grade2_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "good_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_good_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "good_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_good_science
```

```{r}
set.seed(2019)
perm_grade3_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "good_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_good_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "good_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_good_science
```

```{r}
set.seed(2019)
perm_grade5_good_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "good_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_good_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Higher level science
18. I am considering taking higher level courses in science.

YES
```{r}
grade1_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "higherlevel_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_higherlevel_science
```

```{r}
set.seed(2019)
perm_grade1_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "higherlevel_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_higherlevel_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "higherlevel_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_higherlevel_science
```

```{r}
set.seed(2019)
perm_grade2_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "higherlevel_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_higherlevel_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "higherlevel_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_higherlevel_science
```

```{r}
set.seed(2019)
perm_grade3_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "higherlevel_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_higherlevel_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "higherlevel_science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_higherlevel_science
```

```{r}
set.seed(2019)
perm_grade5_higherlevel_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "higherlevel_science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_higherlevel_science %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Science courses
19. I would like the opportunity to take more science courses.

```{r}
grade1_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "science_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_science_courses
```

YES
```{r}
grade2_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_science_courses
```

```{r}
set.seed(2019)
perm_grade2_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "science_courses") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_science_courses %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_science_courses
```

```{r}
set.seed(2019)
perm_grade3_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "science_courses") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_science_courses %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_courses") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_science_courses
```

```{r}
set.seed(2019)
perm_grade5_science_courses <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "science_courses") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_science_courses %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


# EGR 

### New Products
20. I Iike to imagine myself creating new products.

YES
```{r}
grade1_new_products <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "new_products") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_new_products
```

```{r}
set.seed(2019)
perm_grade1_new_products <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "new_products") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_new_products %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade2_new_products <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "new_products") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_new_products
```

```{r}
grade3_new_products <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "new_products") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_new_products
```

YES
```{r}
grade5_new_products <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "new_products") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_new_products
```

```{r}
set.seed(2019)
perm_grade5_new_products <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "new_products") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_new_products %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Engineering Everyday
21. If I learn engineering, then I can improve the things that people use every day.

YES
```{r}
grade1_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "engineering_everyday") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_engineering_everyday
```

```{r}
set.seed(2019)
perm_grade1_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "engineering_everyday") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_engineering_everyday %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "engineering_everyday") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_engineering_everyday
```

```{r}
set.seed(2019)
perm_grade2_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "engineering_everyday") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_engineering_everyday %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "engineering_everyday") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_engineering_everyday
```

```{r}
set.seed(2019)
perm_grade3_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "engineering_everyday") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_engineering_everyday %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "engineering_everyday") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all))
grade5_engineering_everyday
```

```{r}
grade5_engineering_everyday$pre_or_post <- factor(grade5_engineering_everyday$pre_or_post, levels = c("Pre", "Post"))

tiff("engineering_everyday.tiff", units="in", width=7, height=9, res=300)
ggplot(data = grade5_engineering_everyday, mapping = aes(x = pre_or_post, y = mean)) +
  geom_bar(stat = "identity", fill = "slategray4") +
    labs(title = "If I learn engineering, then I can 
improve the things that people use every day.", subtitle = "11th graders", x = "", y = "Average Positivity Towards STEM") +
  theme(plot.title = element_text(size = 22),
  plot.subtitle = element_text(size = 18),
  axis.text=element_text(size=16),
  axis.title=element_text(size=20),
  legend.title=element_text(size=18),
  legend.text=element_text(size=16),
  strip.text=element_text(size=14),
  legend.position ="none")
dev.off()
```

```{r}
set.seed(2019)
perm_grade5_engineering_everyday <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "engineering_everyday") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_engineering_everyday %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Enjoy Building
22. I enjoy building and fixing things.

YES
```{r}
grade1_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "enjoy_building") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_enjoy_building
```

```{r}
set.seed(2019)
perm_grade1_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "enjoy_building") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_enjoy_building %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade2_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "enjoy_building") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_enjoy_building
```

YES
```{r}
grade3_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "enjoy_building") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_enjoy_building
```

```{r}
set.seed(2019)
perm_grade3_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "enjoy_building") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_enjoy_building %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "enjoy_building") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_enjoy_building
```

```{r}
grade5_enjoy_building$pre_or_post <- factor(grade5_enjoy_building$pre_or_post, levels = c("Pre", "Post"))

tiff("enjoy_building.tiff", units="in", width=7, height=9, res=300)
ggplot(data = grade5_enjoy_building, mapping = aes(x = pre_or_post, y = mean)) +
  geom_bar(stat = "identity", fill = "slategray4") +
    labs(title = "I enjoy building and fixing things", subtitle = "11th graders", x = "", y = "Average Positivity Towards STEM") +
  theme(plot.title = element_text(size = 22),
  plot.subtitle = element_text(size = 18),
  axis.text=element_text(size=16),
  axis.title=element_text(size=20),
  legend.title=element_text(size=18),
  legend.text=element_text(size=16),
  strip.text=element_text(size=14),
  legend.position ="none")
dev.off()
```

```{r}
set.seed(2019)
perm_grade5_enjoy_building <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "enjoy_building") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_enjoy_building %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Interested machines
23. I am interested in how certain machines work.

YES
```{r}
grade1_interested_machines <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "interested_machines") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_interested_machines
```

```{r}
set.seed(2019)
perm_grade1_interested_machines <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "interested_machines") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_interested_machines %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_interested_machines <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "interested_machines") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_interested_machines
```

```{r}
set.seed(2019)
perm_grade2_interested_machines <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "interested_machines") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_interested_machines %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_interested_machines <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "interested_machines") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_interested_machines
```

```{r}
set.seed(2019)
perm_grade3_interested_machines <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "interested_machines") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_interested_machines %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade5_interested_machines<- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "interested_machines") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_interested_machines
```

### Career Design
24. Designing products or structures will be important for my future career.

YES
```{r}
grade1_careerdesign <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "career_design") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_careerdesign
```

```{r}
set.seed(2019)
perm_grade1_careerdesign <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "career_design") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_careerdesign %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_careerdesign <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "career_design") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_careerdesign
```

```{r}
set.seed(2019)
perm_grade2_careerdesign <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "career_design") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_careerdesign %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade3_careerdesign <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "career_design") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_careerdesign
```

```{r}
grade5_careerdesign <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "career_design") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_careerdesign
```

### Curiosity Tech
25. I'm curious about how electronics work.

YES
```{r}
grade1_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "curiosity_tech") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_curiosity_tech
```

```{r}
set.seed(2019)
perm_grade1_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "curiosity_tech") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_curiosity_tech %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "curiosity_tech") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_curiosity_tech
```

```{r}
set.seed(2019)
perm_grade2_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "curiosity_tech") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_curiosity_tech %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "curiosity_tech") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_curiosity_tech
```

```{r}
set.seed(2019)
perm_grade3_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "curiosity_tech") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_curiosity_tech %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "curiosity_tech") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_curiosity_tech
```

```{r}
set.seed(2019)
perm_grade5_curiosity_tech <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "curiosity_tech") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_curiosity_tech %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


### Future Innovation
26. I would like to use creativity and innovation in my future work.

```{r}
grade1_future_innovation <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "future_innovation") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_future_innovation
```

YES
```{r}
grade2_future_innovation <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "future_innovation") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_future_innovation
```

```{r}
set.seed(2019)
perm_grade2_future_innovation <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "future_innovation") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_future_innovation %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade3_future_innovation <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "future_innovation") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_future_innovation
```

YES
```{r}
grade5_future_innovation <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "future_innovation") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_future_innovation
```

```{r}
set.seed(2019)
perm_grade5_future_innovation <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "future_innovation") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_future_innovation %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Math science useful
27. Knowing how to use mathematics and science together will allow me to invent useful things.

```{r}
grade1_mathscience_useful <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "mathscience_useful") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_mathscience_useful
```

YES
```{r}
grade2_mathscience_useful <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "mathscience_useful") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_mathscience_useful
```

```{r}
set.seed(2019)
perm_grade2_mathscience_useful <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "mathscience_useful") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_mathscience_useful %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade3_mathscience_useful <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "mathscience_useful") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_mathscience_useful
```

YES
```{r}
grade5_mathscience_useful <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "mathscience_useful") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_mathscience_useful
```

```{r}
set.seed(2019)
perm_grade5_mathscience_useful <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "mathscience_useful") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_mathscience_useful %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Success engineering
28. I think I can succeed in an engineering career.

YES
```{r}
grade1_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "success_engineering") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_success_engineering
```

```{r}
set.seed(2019)
perm_grade1_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "success_engineering") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_success_engineering %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "success_engineering") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_success_engineering
```

```{r}
set.seed(2019)
perm_grade2_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "success_engineering") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_success_engineering %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "success_engineering") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_success_engineering
```

```{r}
set.seed(2019)
perm_grade3_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "success_engineering") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_success_engineering %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "success_engineering") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_success_engineering
```

```{r}
set.seed(2019)
perm_grade5_success_engineering <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "success_engineering") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_success_engineering %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

# I can build
29. I am good at building and fixing things.

YES
```{r}
grade1_i_can_build <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "i_can_build") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_i_can_build
```

```{r}
set.seed(2019)
perm_grade1_i_can_build <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "i_can_build") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_i_can_build %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

```{r}
grade2_i_can_build <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "i_can_build") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_i_can_build
```

```{r}
grade3_i_can_build <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "i_can_build") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_i_can_build
```

YES
```{r}
grade5_i_can_build <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "i_can_build") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_i_can_build
```

```{r}
grade5_i_can_build$pre_or_post <- factor(grade5_i_can_build$pre_or_post, levels = c("Pre", "Post"))

tiff("i_can_build.tiff", units="in", width=7, height=9, res=300)
ggplot(data = grade5_i_can_build, mapping = aes(x = pre_or_post, y = mean)) +
  geom_bar(stat = "identity", fill = "slategray4") +
    labs(title = "I am good at building and fixing things", subtitle = "11th graders", x = "", y = "Average Positivity Towards STEM") +
  theme(plot.title = element_text(size = 22),
  plot.subtitle = element_text(size = 18),
  axis.text=element_text(size=16),
  axis.title=element_text(size=20),
  legend.title=element_text(size=18),
  legend.text=element_text(size=16),
  strip.text=element_text(size=14),
  legend.position ="none")
dev.off()
```

```{r}
set.seed(2019)
perm_grade5_i_can_build <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "i_can_build") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_i_can_build %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

### Opportunity egr
30. I would like the opportunity to take more engineering courses.

YES
```{r}
grade1_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "opportunity") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_opportunity
```

```{r}
set.seed(2019)
perm_grade1_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "opportunity") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_opportunity %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade2_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "opportunity") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_opportunity
```

```{r}
set.seed(2019)
perm_grade2_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "opportunity") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_opportunity %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade3_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "opportunity") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_opportunity
```

```{r}
set.seed(2019)
perm_grade3_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "opportunity") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_opportunity %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

YES
```{r}
grade5_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "opportunity") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_opportunity
```

```{r}
set.seed(2019)
perm_grade5_opportunity <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "opportunity") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_opportunity %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


# OTHERS

# Grade 1

## Contribute Community 

```{r}
grade1_contribute_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "contribute_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_contribute_community
```

## Resolve Problems Community 

```{r}
grade1_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "resolve_problems_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_resolve_problems_community
```

## External Help 

```{r}
grade1_external_help <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "external_help") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_external_help
```

## Leader Community 

```{r}
grade1_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "leader_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_leader_community
```

```{r}
set.seed(2019)
perm_grade1_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "leader_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade1_leader_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Contribute Community .1

```{r}
grade1_contribute_community.1 <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  filter(question == "contribute_community.1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade1_contribute_community.1
```

## Grade 2

## Contribute Community

```{r}
grade2_contribute_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "contribute_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_contribute_community
```

```{r}
set.seed(2019)
perm_grade2_contribute_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "contribute_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_contribute_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Resolve Problems Community 

```{r}
grade2_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "resolve_problems_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_resolve_problems_community
```

```{r}
set.seed(2019)
perm_grade2_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "resolve_problems_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_resolve_problems_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## External Help 

```{r}
grade2_external_help <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "external_help") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_external_help
```

## Leader Community 

```{r}
grade2_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "leader_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_leader_community
```

```{r}
set.seed(2019)
perm_grade2_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "leader_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_leader_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Contribute Community .1

```{r}
grade2_contribute_community.1 <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "contribute_community.1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade2_contribute_community.1
```
```{r}
set.seed(2019)
perm_grade2_contribute_community.1 <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  filter(question == "contribute_community.1") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade2_contribute_community.1 %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Grade 3

## Contribute Community

```{r}
grade3_contribute_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "contribute_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_contribute_community
```

```{r}
set.seed(2019)
perm_grade3_contribute_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "contribute_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_contribute_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


## Resolve Problems Community 

```{r}
grade3_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "resolve_problems_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_resolve_problems_community
```

```{r}
set.seed(2019)
perm_grade3_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "resolve_problems_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_resolve_problems_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## External Help 

```{r}
grade3_external_help <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "external_help") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_external_help
```

```{r}
set.seed(2019)
perm_grade3_external_help <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "external_help") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_external_help %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Leader Community 

```{r}
grade3_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "leader_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_leader_community
```

```{r}
set.seed(2019)
perm_grade3_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "leader_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_leader_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Contribute Community .1

```{r}
grade3_contribute_community.1 <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "contribute_community.1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade3_contribute_community.1
```

```{r}
set.seed(2019)
perm_grade3_contribute_community.1 <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  filter(question == "contribute_community.1") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade3_contribute_community.1 %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Grade 5

## Contribute Community

```{r}
grade5_contribute_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "contribute_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_contribute_community
```

## Resolve Problems Community 

```{r}
grade5_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "resolve_problems_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_resolve_problems_community
```

```{r}
set.seed(2019)
perm_grade5_resolve_problems_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "resolve_problems_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_resolve_problems_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## External Help 

```{r}
grade5_external_help <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "external_help") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_external_help
```


## Leader Community 

```{r}
grade5_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "leader_community") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_leader_community
```

```{r}
set.seed(2019)
perm_grade5_leader_community <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "leader_community") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_grade5_leader_community %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## Contribute Community .1

```{r}
grade5_contribute_community.1 <- others %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  filter(question == "contribute_community.1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean))
grade5_contribute_community.1
```