---
title: "Data Exploration"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)
```

# Load packages
```{r load-packages, message=FALSE}
library(tidyverse)
library(ggplot2)
library(shiny)
library(infer)
library(data.table)
```

# Load data
```{r load-data}
pre_empower <- read.csv("data/PRE_Empowerment.csv",
                    sep = ";")
post_empower <- read.csv("data/POST_Empowerment.csv",
                    sep = ";")
pre_2019 <- read.csv("data/PRE2019.csv",
                    sep = ";")
post_2019 <- read.csv("data/POST2019.csv",
                    sep = ";")
```

## Include columns that indicate whether responses are from pre- or post-implementation surveys, and what year they were collected
```{r data}
pre_empower <- pre_empower %>%
  mutate(pre_or_post = "Pre") %>%
  mutate(year = "2018")
post_empower <- post_empower %>%
  mutate(pre_or_post = "Post") %>%
  mutate(year = "2018")
pre_2019 <- pre_2019 %>%
  mutate(pre_or_post = "Pre") %>%
  mutate(year = "2019")
post_2019 <- post_2019 %>%
  mutate(pre_or_post = "Post") %>%
  mutate(year = "2019")
```

## Count how many students took the pre- and post-implementation surveys in 2018 and 2019
```{r}
count(pre_empower)
count(post_empower)
count(pre_2019)
count(post_2019)
```

```{r}
pre_empower %>%
  group_by(grade) %>%
  count
post_empower %>%
  group_by(grade) %>%
  count
pre_2019 %>%
  group_by(grade) %>%
  count
post_2019 %>%
  group_by(grade) %>%
  count
```


## Join pre- and post-implementation data into one dataset. Then join data from 2018 and 2019 into one dataset
```{r}
empower_2018 <- full_join(pre_empower, post_empower) %>%
  select(-c(other_plan_afterschool))
empower_2019 <- full_join(pre_2019, post_2019) %>%
  select(-c(other_plan_afterschool))
empower_2019$grade <- as.factor(empower_2019$grade)
empower <- full_join(empower_2018, empower_2019)
```

## Rename to positive vs. negative feelings from A, B, C, D, E (as they were on the survey) to 1, 2, 3, 4, 5
```{r change-names}
change_names <- function(naming){
naming %>%
  str_replace("A", "1") %>%
  str_replace("B", "2") %>%
  str_replace("C", "3") %>%
  str_replace("D", "4") %>%
  str_replace("E", "5")
}

empower$math_worst <- change_names(empower$math_worst)
empower$math_career <- change_names(empower$math_career)
empower$not_enjoy_math <- change_names(empower$not_enjoy_math)
empower$good_at_math <- change_names(empower$good_at_math)
empower$decentschool_badmath <- change_names(empower$decentschool_badmath)
empower$higherlevel_math <- change_names(empower$higherlevel_math)
empower$good_math_grades <- change_names(empower$good_math_grades)
empower$interesting_math <- change_names(empower$interesting_math)
empower$future_math <- change_names(empower$future_math)
empower$math_courses <- change_names(empower$math_courses)
empower$sure_science <- change_names(empower$sure_science)
empower$science_career <- change_names(empower$science_career)
empower$science_outsideofschool <- change_names(empower$science_outsideofschool)
empower$science_pay <- change_names(empower$science_pay)
empower$science_job <- change_names(empower$science_job)
empower$good_science <- change_names(empower$good_science)
empower$decentschool_badscience <- change_names(empower$decentschool_badscience)
empower$higherlevel_science <- change_names(empower$higherlevel_science)
empower$science_courses <- change_names(empower$science_courses)
empower$new_products <- change_names(empower$new_products)
empower$engineering_everyday <- change_names(empower$engineering_everyday)
empower$enjoy_building <- change_names(empower$enjoy_building)
empower$interested_machines <- change_names(empower$interested_machines)
empower$career_design <- change_names(empower$career_design)
empower$curiosity_tech <- change_names(empower$curiosity_tech)
empower$future_innovation <- change_names(empower$future_innovation)
empower$mathscience_useful <- change_names(empower$mathscience_useful)
empower$success_engineering <- change_names(empower$success_engineering)
empower$i_can_build <- change_names(empower$i_can_build)
empower$opportunity_engineering <- change_names(empower$opportunity_engineering)
empower$contribute_community <- change_names(empower$contribute_community)
empower$resolve_problems_community <- change_names(empower$resolve_problems_community)
empower$external_help <- change_names(empower$external_help)
empower$leader_community <- change_names(empower$leader_community)
empower$contribute_community.1 <- change_names(empower$contribute_community.1)
```

## Create different datasets for each question that will be analyzed. Each dataset should have the variables: "pre_or_post", "all" (the response - whether students feel positively or negatively towards the question), "grade" (the respondent's grade level), and "class" (which classifies which course the question refers to - EGR, math, or science)

### EGR
```{r}
new_products <- empower %>%
  select(pre_or_post, new_products, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "new_products")
names(new_products) <- c("pre_or_post", "all", "grade", "class", "question")

engineering_everyday <- empower %>%
  select(pre_or_post, engineering_everyday, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "engineering_everyday")
names(engineering_everyday) <- c("pre_or_post", "all", "grade", "class", "question")

enjoy_building <- empower %>%
  select(pre_or_post, enjoy_building, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "enjoy_building")
names(enjoy_building) <- c("pre_or_post", "all", "grade", "class", "question")

interested_machines <- empower %>%
  select(pre_or_post, interested_machines, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "interested_machines")
names(interested_machines) <- c("pre_or_post", "all", "grade", "class", "question")

career_design <- empower %>%
  select(pre_or_post, career_design, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "career_design")
names(career_design) <- c("pre_or_post", "all", "grade", "class", "question")

curiosity_tech <- empower %>%
  select(pre_or_post, curiosity_tech, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "curiosity_tech")
names(curiosity_tech) <- c("pre_or_post", "all", "grade", "class", "question")

future_innovation <- empower %>%
  select(pre_or_post, future_innovation, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "future_innovation")
names(future_innovation) <- c("pre_or_post", "all", "grade", "class", "question")

mathscience_useful <- empower %>%
  select(pre_or_post, mathscience_useful, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "mathscience_useful")
names(mathscience_useful) <- c("pre_or_post", "all", "grade", "class", "question")

success_engineering <- empower %>%
  select(pre_or_post, success_engineering, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "success_engineering")
names(success_engineering) <- c("pre_or_post", "all", "grade", "class", "question")

i_can_build <- empower %>%
  select(pre_or_post, i_can_build, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "i_can_build")
names(i_can_build) <- c("pre_or_post", "all", "grade", "class", "question")

opportunity_engineering <- empower %>%
  select(pre_or_post, opportunity_engineering, grade) %>%
  mutate(class = "Engineering and Technology") %>%
  mutate(question = "opportunity")
names(opportunity_engineering) <- c("pre_or_post", "all", "grade", "class", "question")
```

### Science
```{r}
sure_science <- empower %>%
  select(pre_or_post, sure_science, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "sure_science")
names(sure_science) <- c("pre_or_post", "all", "grade", "class", "question")

science_career <- empower %>%
  select(pre_or_post, science_career, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_career")
names(science_career) <- c("pre_or_post", "all", "grade", "class", "question")

science_outsideofschool <- empower %>%
  select(pre_or_post, science_outsideofschool, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_outsideofschool")
names(science_outsideofschool) <- c("pre_or_post", "all", "grade", "class", "question")

science_pay <- empower %>%
  select(pre_or_post, science_pay, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_pay")
names(science_pay) <- c("pre_or_post", "all", "grade", "class", "question")

science_job <- empower %>%
  select(pre_or_post, science_job, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_job")
names(science_job) <- c("pre_or_post", "all", "grade", "class", "question")

good_science <- empower %>%
  select(pre_or_post, good_science, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "good_science")
names(good_science) <- c("pre_or_post", "all", "grade", "class", "question")

higherlevel_science <- empower %>%
  select(pre_or_post, higherlevel_science, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "higherlevel_science")
names(higherlevel_science) <- c("pre_or_post", "all", "grade", "class", "question")

science_courses <- empower %>%
  select(pre_or_post, science_courses, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "science_courses")
names(science_courses) <- c("pre_or_post", "all", "grade", "class", "question")

decentschool_badscience <- empower %>%
  select(pre_or_post, decentschool_badscience, grade) %>%
  mutate(class = "Science") %>%
  mutate(question = "decentschool_badscience")
names(decentschool_badscience) <- c("pre_or_post", "all", "grade", "class", "question")
```


### Math
```{r}
math_career <- empower %>%
  select(pre_or_post, math_career, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "math_career")
names(math_career) <- c("pre_or_post", "all", "grade", "class", "question")

good_at_math <- empower %>%
  select(pre_or_post, good_at_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "good_at_math")
names(good_at_math) <- c("pre_or_post", "all", "grade", "class", "question")

higherlevel_math <- empower %>%
  select(pre_or_post, higherlevel_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "higherlevel_math")
names(higherlevel_math) <- c("pre_or_post", "all", "grade", "class", "question")

good_math_grades <- empower %>%
  select(pre_or_post, good_math_grades, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "good_math_grades")
names(good_math_grades) <- c("pre_or_post", "all", "grade", "class", "question")

interesting_math <- empower %>%
  select(pre_or_post, interesting_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "interesting_math")
names(interesting_math) <- c("pre_or_post", "all", "grade", "class", "question")

future_math <- empower %>%
  select(pre_or_post, future_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "future_math")
names(future_math) <- c("pre_or_post", "all", "grade", "class", "question")

math_courses <- empower %>%
  select(pre_or_post, math_courses, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "math_courses")
names(math_courses) <- c("pre_or_post", "all", "grade", "class", "question")

math_worst <- empower %>%
  select(pre_or_post, math_worst, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "math_worst")
names(math_worst) <- c("pre_or_post", "all", "grade", "class", "question")

not_enjoy_math <- empower %>%
  select(pre_or_post, not_enjoy_math, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "not_enjoy_math")
names(not_enjoy_math) <- c("pre_or_post", "all", "grade", "class", "question")

decentschool_badmath <- empower %>%
  select(pre_or_post, decentschool_badmath, grade) %>%
  mutate(class = "Math") %>%
  mutate(question = "decentschool_badmath")
names(decentschool_badmath) <- c("pre_or_post", "all", "grade", "class", "question")
```

### Helping community

```{r}
contribute_community <- empower %>%
  select(pre_or_post, contribute_community, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "contribute_community")
names(contribute_community) <- c("pre_or_post", "all", "grade", "class", "question")

resolve_problems_community <- empower %>%
  select(pre_or_post, resolve_problems_community, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "resolve_problems_community")
names(resolve_problems_community) <- c("pre_or_post", "all", "grade", "class", "question")

external_help <- empower %>%
  select(pre_or_post, external_help, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "external_help")
names(external_help) <- c("pre_or_post", "all", "grade", "class", "question")

leader_community <- empower %>%
  select(pre_or_post, leader_community, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "leader_community")
names(leader_community) <- c("pre_or_post", "all", "grade", "class", "question")

contribute_community.1 <- empower %>%
  select(pre_or_post, contribute_community.1, grade) %>%
  mutate(class = "Others") %>%
  mutate(question = "contribute_community.1")
names(contribute_community.1) <- c("pre_or_post", "all", "grade", "class", "question")
```


```{r}
together <- rbind(new_products,
             engineering_everyday,
             enjoy_building,
             interested_machines,
             career_design,
             curiosity_tech,
             future_innovation,
             mathscience_useful,
             success_engineering,
             i_can_build,
             opportunity_engineering, 
             sure_science,
             science_career, 
             science_outsideofschool,
             science_pay,
             science_job,
             good_science,
             higherlevel_science,
             science_courses,
             math_career,
             good_at_math,
             higherlevel_math,
             good_math_grades,
             interesting_math,
             future_math,
             math_courses)
```

```{r}
others <- rbind(math_worst, 
                not_enjoy_math,
                decentschool_badmath,
                decentschool_badscience,
                contribute_community,
                resolve_problems_community,
                external_help,
                leader_community,
                contribute_community.1)
```


```{r}
together$grade <- together$grade %>%
  str_replace("5 bach", "5") %>%
  str_replace("5 mag", "5")
together <- transform(together, all = as.numeric(all))
```

```{r}
together %>%
  filter(!is.na(all)) %>%
  group_by(pre_or_post) %>%
  count(question)
```

```{r}
observations1 <- together %>%
  group_by(question, pre_or_post, grade) %>%
  filter(!is.na(all)) %>%
  count()
observations1
```

```{r}
others$grade <- others$grade %>%
  str_replace("5 bach", "5") %>%
  str_replace("5 mag", "5")
others <- transform(others, all = as.numeric(all))
```

```{r}
observations2 <- others %>%
  group_by(question, pre_or_post, grade) %>%
  filter(!is.na(all)) %>%
  count()
observations2
```

```{r}
sum_of_scores <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(grade)) %>%
  group_by(question, pre_or_post, grade) %>%
  summarize(Sum = sum(all))
sum_of_scores
```





