---
title: "Empowerment Survey"
output: 
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load packages
```{r load-packages, message=FALSE}
library(tidyverse)
library(broom)
library(infer)
library(ggplot2)
```

### Background Information
This survey was conducted on 143 girls in an all-female boarding school in Guatemala before and after a pair of Duke students conducted STEM-focused courses. Grade 1 would be equivalent to 7th grade in the American school system. We taught girls in grades 1, 2, and 3 the same curriculum, and girls in grades 5 magisterio (mag) and 5 bachillerato (bach) another curriculum. In 2017, the girls in 5 magisterio and 5 bachillerato took the curriculum that grades 1, 2, and 3 took in 2018. The girls in 5 magisterio are on a program specifically to become school teachers. The girls in 5 bachillerato usually pursue careers other than teaching. 

### Purpose
The purpose of the course is to give girls the chance to explore STEM-related courses and help them realize that they are capable of pursuing STEM-related careers, if they want to. 

Thus, the purpose of the survey is to evaluate the girls' attitudes towards STEM and STEM-related careers before and after the course. 

### A note for Professor Tackett
I feel like a have a lot of interesting data and visualizations, but I am unsure about what direction to take the statistical research in order to come to important conclusions about the curriculum. 

I am thinking that some of the important takeaways could be observations about how the program's effect differs: 
- Between older and younger girls (middle vs. high school)
- Between different grade levels (more specific than just saying younger vs. older)
- Between girls who are on the teaching-specific program (5 magisterio) vs. those who might have time to decide on their career path (5 bach and grades 1-3)
- Between girls who took the course last year and those who did not 

However, I am stuck on how to decide which of these paths to pursue. 

Furthermore, the lab through which I am doing this investigation failed to send me the Post-Implementation survey for 2017, so I only have the Pre-Implementation survey for 2017. The survey in 2017 was much shorter. However, we might be able to draw some comparisons between 2017 and 2018, once I get all the 2017 data. 

Finally, how do I factor in things that were not directly addressed in the survey? For example, at Flunch we talked about how the girls might have felt inclined to answer the post-implementation survey more positively because they liked their teachers, not necessarily because they liked the subject. 

### Load data
```{r load-data}
pre_empower <- read.csv("data/PRE_Empowerment.csv",
                    sep = ";")
post_empower <- read.csv("data/POST_Empowerment.csv",
                    sep = ";")
```

# SECTION 1: ORGANIZING DATA
### Classifying and joining pre and post responses 
```{r data}
pre_empower <- pre_empower %>%
  mutate(pre_or_post = "pre")
post_empower <- post_empower %>%
  mutate(pre_or_post = "post")
```

```{r join-data}
empower <- full_join(pre_empower, post_empower)
```

### Rank
```{r id-numbers}
empower$ID <- seq.int(nrow(empower))
```

### Changing responses from letters to words and characterizing them as "Positive" or "Negative" 

To reduce the variability of the data, I joined the answers "Absolutely" with "Yes" to define someone who feels positively about a certain question. I joined "No" with "Absolutely Not" to define someone who feels negatively about a certain question. 

```{r change-names}
change_names <- function(naming){
naming %>%
  str_replace("A", "no") %>%
  str_replace("B", "no") %>%
  str_replace("C", "neutral") %>%
  str_replace("D", "yes") %>%
  str_replace("E", "yes")
}

change_names2 <- function(naming){
naming %>%
  str_replace("A", "very good") %>%
  str_replace("B", "okay") %>%
  str_replace("C", "bad")
}

change_names3 <- function(naming){
naming %>%
  str_replace("A", "yes") %>%
  str_replace("B", "no") %>%
  str_replace("C", "not sure")
}

empower$math_worst <- change_names(empower$math_worst)
empower$math_career <- change_names(empower$math_career)
empower$not_enjoy_math <- change_names(empower$not_enjoy_math)
empower$good_at_math <- change_names(empower$good_at_math)
empower$decentschool_badmath <- change_names(empower$decentschool_badmath)
empower$higherlevel_math <- change_names(empower$higherlevel_math)
empower$good_math_grades <- change_names(empower$good_math_grades)
empower$interesting_math <- change_names(empower$interesting_math)
empower$future_math <- change_names(empower$future_math)
empower$math_courses <- change_names(empower$math_courses)
empower$sure_science <- change_names(empower$sure_science)
empower$science_career <- change_names(empower$science_career)
empower$science_outsideofschool <- change_names(empower$science_outsideofschool)
empower$science_pay <- change_names(empower$science_pay)
empower$science_job <- change_names(empower$science_job)
empower$good_science <- change_names(empower$good_science)
empower$decentschool_badscience <- change_names(empower$decentschool_badscience)
empower$higherlevel_science <- change_names(empower$higherlevel_science)
empower$science_courses <- change_names(empower$science_courses)
empower$new_products <- change_names(empower$new_products)
empower$engineering_everyday <- change_names(empower$engineering_everyday)
empower$enjoy_building <- change_names(empower$enjoy_building)
empower$interested_machines <- change_names(empower$interested_machines)
empower$career_design <- change_names(empower$career_design)
empower$curiosity_tech <- change_names(empower$curiosity_tech)
empower$future_innovation <- change_names(empower$future_innovation)
empower$mathscience_useful <- change_names(empower$mathscience_useful)
empower$success_engineering <- change_names(empower$success_engineering)
empower$i_can_build <- change_names(empower$i_can_build)
empower$opportunity_engineering <- change_names(empower$opportunity_engineering)
empower$contribute_community <- change_names(empower$contribute_community)
empower$resolve_problems_community <- change_names(empower$resolve_problems_community)
empower$external_help <- change_names(empower$external_help)
empower$leader_community <- change_names(empower$leader_community)
empower$contribute_community.1 <- change_names(empower$contribute_community.1)

empower$prediction_literature <- change_names2(empower$prediction_literature)
empower$prediction_math <- change_names2(empower$prediction_math)
empower$prediction_science <- change_names2(empower$prediction_science)

empower$future_math_classes <- change_names3(empower$future_math_classes)
empower$future_science_classes <- change_names3(empower$future_science_classes)
empower$future_egr_classes <- change_names3(empower$future_egr_classes)
```

## Selecting data

I excluded variables that showed extreme variance or are not relevant to the study. For example, when they were asked whether their parents had STEM-related careers (parents_stem), many girls classified farming or other agricultural/manual labor as STEM-related careers.

I created a new data set that looks at the grades by age group ("Younger" vs. "Older")
```{r}
empower_new <- empower %>%
  select(-c(parents_stem, 
            which_parent_stem, 
            parent_profession, 
            number_science_classes, 
            number_math_classes, 
            number_tech_classes, 
            number_egr_classes))
empower_byage <- empower_new %>%
  mutate(age_groups = case_when(
    grade == "1" ~ "younger",
    grade == "2" ~ "younger",
    grade == "3" ~ "younger",
    grade == "5 bach" ~ "older",
    grade == "5 mag" ~ "older"
  ))
```

# SECTION 2: PROPORTION OF GIRLS THAT RESPOND POSITIVELY TO STEM 

## PRE Attitudes towards math

This section finds the proportion of girls in each grade who answered positively questions that related to math in the pre-implementation survey.

### Grade 1 
```{r}
pre_empower_math1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "pre")
pre_empower_math1$math <- paste(pre_empower_math1$math_career, pre_empower_math1$good_at_math, pre_empower_math1$higherlevel_math, pre_empower_math1$good_math_grades, pre_empower_math1$interesting_math, pre_empower_math1$future_math, pre_empower_math1$math_courses)

pre_math_prop1 <- sum(str_count(pre_empower_math1$math, "yes")) / (sum(str_count(pre_empower_math1$math, "no")) + sum(str_count(pre_empower_math1$math, "yes")))
pre_math_prop1
```

### Grade 2

```{r}
pre_empower_math2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "pre")
pre_empower_math2$math <- paste(pre_empower_math2$math_career, pre_empower_math2$good_at_math, pre_empower_math2$higherlevel_math, pre_empower_math2$good_math_grades, pre_empower_math2$interesting_math, pre_empower_math2$future_math, pre_empower_math2$math_courses)

pre_math_prop2 <- sum(str_count(pre_empower_math2$math, "yes")) / (sum(str_count(pre_empower_math2$math, "no")) + sum(str_count(pre_empower_math2$math, "yes")))
pre_math_prop2
```

### Grade 3

```{r}
pre_empower_math3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "pre")
pre_empower_math3$math <- paste(pre_empower_math3$math_career, pre_empower_math3$good_at_math, pre_empower_math3$higherlevel_math, pre_empower_math3$good_math_grades, pre_empower_math3$interesting_math, pre_empower_math3$future_math, pre_empower_math3$math_courses)

pre_math_prop3 <- sum(str_count(pre_empower_math3$math, "yes")) / (sum(str_count(pre_empower_math3$math, "no")) + sum(str_count(pre_empower_math3$math, "yes")))
pre_math_prop3
```

### Grade 5 magisterio

```{r}
pre_empower_math5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "pre")
pre_empower_math5m$math <- paste(pre_empower_math5m$math_career, pre_empower_math5m$good_at_math, pre_empower_math5m$higherlevel_math, pre_empower_math5m$good_math_grades, pre_empower_math5m$interesting_math, pre_empower_math5m$future_math, pre_empower_math5m$math_courses)

pre_math_prop5m <- sum(str_count(pre_empower_math5m$math, "yes")) / (sum(str_count(pre_empower_math5m$math, "no")) + sum(str_count(pre_empower_math5m$math, "yes")))
pre_math_prop5m
```

### Grade 5 bachillerato

```{r}
pre_empower_math5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "pre")
pre_empower_math5b$math <- paste(pre_empower_math5b$math_career, pre_empower_math5b$good_at_math, pre_empower_math5b$higherlevel_math, pre_empower_math5b$good_math_grades, pre_empower_math5b$interesting_math, pre_empower_math5b$future_math, pre_empower_math5b$math_courses)

pre_math_prop5b <- sum(str_count(pre_empower_math5b$math, "yes")) / (sum(str_count(pre_empower_math5b$math, "no")) + sum(str_count(pre_empower_math5b$math, "yes")))
pre_math_prop5b
```

## PRE Attitudes towards science

The next section finds the proportion of girls in each grade who answered positively questions that related to science in the pre-implementation survey.

### Grade 1

```{r}
pre_empower_science1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "pre")
pre_empower_science1$science <- paste(pre_empower_science1$sure_science, pre_empower_science1$science_career, pre_empower_science1$science_outsideofschool, pre_empower_science1$science_pay, pre_empower_science1$science_job, pre_empower_science1$good_science, pre_empower_science1$higherlevel_science, pre_empower_science1$science_courses)

pre_science_prop1 <- sum(str_count(pre_empower_science1$science, "yes")) / (sum(str_count(pre_empower_science1$science, "no")) + sum(str_count(pre_empower_science1$science, "yes")))
pre_science_prop1
```

### Grade 2

```{r}
pre_empower_science2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "pre")
pre_empower_science2$science <- paste(pre_empower_science2$sure_science, pre_empower_science2$science_career, pre_empower_science2$science_outsideofschool, pre_empower_science2$science_pay, pre_empower_science2$science_job, pre_empower_science2$good_science, pre_empower_science2$higherlevel_science, pre_empower_science2$science_courses)

pre_science_prop2 <- sum(str_count(pre_empower_science2$science, "yes")) / (sum(str_count(pre_empower_science2$science, "no")) + sum(str_count(pre_empower_science2$science, "yes")))
pre_science_prop2
```
### Grade 3

```{r}
pre_empower_science3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "pre")
pre_empower_science3$science <- paste(pre_empower_science3$sure_science, pre_empower_science3$science_career, pre_empower_science3$science_outsideofschool, pre_empower_science3$science_pay, pre_empower_science3$science_job, pre_empower_science3$good_science, pre_empower_science3$higherlevel_science, pre_empower_science3$science_courses)

pre_science_prop3 <- sum(str_count(pre_empower_science3$science, "yes")) / (sum(str_count(pre_empower_science3$science, "no")) + sum(str_count(pre_empower_science3$science, "yes")))
pre_science_prop3
```

### Grade 5 magisterio

```{r}
pre_empower_science5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "pre")
pre_empower_science5m$science <- paste(pre_empower_science5m$sure_science, pre_empower_science5m$science_career, pre_empower_science5m$science_outsideofschool, pre_empower_science5m$science_pay, pre_empower_science5m$science_job, pre_empower_science5m$good_science, pre_empower_science5m$higherlevel_science, pre_empower_science5m$science_courses)

pre_science_prop5m <- sum(str_count(pre_empower_science5m$science, "yes")) / (sum(str_count(pre_empower_science5m$science, "no")) + sum(str_count(pre_empower_science5m$science, "yes")))
pre_science_prop5m
```

### Grade 5 bachillerato

```{r}
pre_empower_science5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "pre")
pre_empower_science5b$science <- paste(pre_empower_science5b$sure_science, pre_empower_science5b$science_career, pre_empower_science5b$science_outsideofschool, pre_empower_science5b$science_pay, pre_empower_science5b$science_job, pre_empower_science5b$good_science, pre_empower_science5b$higherlevel_science, pre_empower_science5b$science_courses)

pre_science_prop5b <- sum(str_count(pre_empower_science5b$science, "yes")) / (sum(str_count(pre_empower_science5b$science, "no")) + sum(str_count(pre_empower_science5b$science, "yes")))
pre_science_prop5b
```

## PRE Attitudes towards engineering

The next section finds the proportion of girls in each grade who answered positively questions that related to engineering in the pre-implementation survey.

### Grade 1

```{r}
pre_empower_egr1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "pre")
pre_empower_egr1$egr <- paste(pre_empower_egr1$new_products, pre_empower_egr1$engineering_everyday, pre_empower_egr1$enjoy_building, pre_empower_egr1$interested_machines, pre_empower_egr1$career_design, pre_empower_egr1$curiosity_tech, pre_empower_egr1$future_innovation, pre_empower_egr1$mathscience_useful, pre_empower_egr1$success_engineering, pre_empower_egr1$i_can_build, pre_empower_egr1$opportunity_engineering)

pre_egr_prop1 <- sum(str_count(pre_empower_egr1$egr, "yes")) / (sum(str_count(pre_empower_egr1$egr, "no")) + sum(str_count(pre_empower_egr1$egr, "yes")))
pre_egr_prop1
```

### Grade 2

```{r}
pre_empower_egr2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "pre")
pre_empower_egr2$egr <- paste(pre_empower_egr2$new_products, pre_empower_egr2$engineering_everyday, pre_empower_egr2$enjoy_building, pre_empower_egr2$interested_machines, pre_empower_egr2$career_design, pre_empower_egr2$curiosity_tech, pre_empower_egr2$future_innovation, pre_empower_egr2$mathscience_useful, pre_empower_egr2$success_engineering, pre_empower_egr2$i_can_build, pre_empower_egr2$opportunity_engineering)

pre_egr_prop2 <- sum(str_count(pre_empower_egr2$egr, "yes")) / (sum(str_count(pre_empower_egr2$egr, "no")) + sum(str_count(pre_empower_egr2$egr, "yes")))
pre_egr_prop2
```

### Grade 3

```{r}
pre_empower_egr3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "pre")
pre_empower_egr3$egr <- paste(pre_empower_egr3$new_products, pre_empower_egr3$engineering_everyday, pre_empower_egr3$enjoy_building, pre_empower_egr3$interested_machines, pre_empower_egr3$career_design, pre_empower_egr3$curiosity_tech, pre_empower_egr3$future_innovation, pre_empower_egr3$mathscience_useful, pre_empower_egr3$success_engineering, pre_empower_egr3$i_can_build, pre_empower_egr3$opportunity_engineering)

pre_egr_prop3 <- sum(str_count(pre_empower_egr3$egr, "yes")) / (sum(str_count(pre_empower_egr3$egr, "no")) + sum(str_count(pre_empower_egr3$egr, "yes")))
pre_egr_prop3
```

### Grade 5 magisterio

```{r}
pre_empower_egr5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "pre")
pre_empower_egr5m$egr <- paste(pre_empower_egr5m$new_products, pre_empower_egr5m$engineering_everyday, pre_empower_egr5m$enjoy_building, pre_empower_egr5m$interested_machines, pre_empower_egr5m$career_design, pre_empower_egr5m$curiosity_tech, pre_empower_egr5m$future_innovation, pre_empower_egr5m$mathscience_useful, pre_empower_egr5m$success_engineering, pre_empower_egr5m$i_can_build, pre_empower_egr5m$opportunity_engineering)

pre_egr_prop5m <- sum(str_count(pre_empower_egr5m$egr, "yes")) / (sum(str_count(pre_empower_egr5m$egr, "no")) + sum(str_count(pre_empower_egr5m$egr, "yes")))
pre_egr_prop5m
```


### Grade 5 bachillerato

```{r}
pre_empower_egr5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "pre")
pre_empower_egr5b$egr <- paste(pre_empower_egr5b$new_products, pre_empower_egr5b$engineering_everyday, pre_empower_egr5b$enjoy_building, pre_empower_egr5b$interested_machines, pre_empower_egr5b$career_design, pre_empower_egr5b$curiosity_tech, pre_empower_egr5b$future_innovation, pre_empower_egr5b$mathscience_useful, pre_empower_egr5b$success_engineering, pre_empower_egr5b$i_can_build, pre_empower_egr5b$opportunity_engineering)

pre_egr_prop5b <- sum(str_count(pre_empower_egr5b$egr, "yes")) / (sum(str_count(pre_empower_egr5b$egr, "no")) + sum(str_count(pre_empower_egr5b$egr, "yes")))
pre_egr_prop5b
```

```{r}
avg_math_pre <- (pre_math_prop1 + pre_math_prop2 + pre_math_prop3 + pre_math_prop5m + pre_math_prop5b)/5
avg_science_pre <- (pre_science_prop1 + pre_science_prop2 + pre_science_prop3 + pre_science_prop5m + pre_science_prop5b)/5
avg_egr_pre <- (pre_egr_prop1 + pre_egr_prop2 + pre_egr_prop3 + pre_egr_prop5m + pre_egr_prop5b)/5
```


## POST Attitudes towards math

The next section finds the proportion of girls in each grade who answered positively questions that related to math in the post-implementation survey.

### Grade 1 
```{r}
empower_math1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "post")
empower_math1$math <- paste(empower_math1$math_career, empower_math1$good_at_math, empower_math1$higherlevel_math, empower_math1$good_math_grades, empower_math1$interesting_math, empower_math1$future_math, empower_math1$math_courses)

math_prop1 <- sum(str_count(empower_math1$math, "yes")) / (sum(str_count(empower_math1$math, "no")) + sum(str_count(empower_math1$math, "yes")))
math_prop1
```

### Grade 2

```{r}
empower_math2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "post")
empower_math2$math <- paste(empower_math2$math_career, empower_math2$good_at_math, empower_math2$higherlevel_math, empower_math2$good_math_grades, empower_math2$interesting_math, empower_math2$future_math, empower_math2$math_courses)

math_prop2 <- sum(str_count(empower_math2$math, "yes")) / (sum(str_count(empower_math2$math, "no")) + sum(str_count(empower_math2$math, "yes")))
math_prop2
```

### Grade 3

```{r}
empower_math3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "post")
empower_math3$math <- paste(empower_math3$math_career, empower_math3$good_at_math, empower_math3$higherlevel_math, empower_math3$good_math_grades, empower_math3$interesting_math, empower_math3$future_math, empower_math3$math_courses)

math_prop3 <- sum(str_count(empower_math3$math, "yes")) / (sum(str_count(empower_math3$math, "no")) + sum(str_count(empower_math3$math, "yes")))
math_prop3
```

### Grade 5 magisterio

```{r}
empower_math5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "post")
empower_math5m$math <- paste(empower_math5m$math_career, empower_math5m$good_at_math, empower_math5m$higherlevel_math, empower_math5m$good_math_grades, empower_math5m$interesting_math, empower_math5m$future_math, empower_math5m$math_courses)

math_prop5m <- sum(str_count(empower_math5m$math, "yes")) / (sum(str_count(empower_math5m$math, "no")) + sum(str_count(empower_math5m$math, "yes")))
math_prop5m
```

### Grade 5 bachillerato

```{r}
empower_math5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "post")
empower_math5b$math <- paste(empower_math5b$math_career, empower_math5b$good_at_math, empower_math5b$higherlevel_math, empower_math5b$good_math_grades, empower_math5b$interesting_math, empower_math5b$future_math, empower_math5b$math_courses)

math_prop5b <- sum(str_count(empower_math5b$math, "yes")) / (sum(str_count(empower_math5b$math, "no")) + sum(str_count(empower_math5b$math, "yes")))
math_prop5b
```

## POST Attitudes towards science

The next section finds the proportion of girls in each grade who answered positively questions that related to science in the post-implementation survey.

### Grade 1

```{r}
empower_science1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "post")
empower_science1$science <- paste(empower_science1$sure_science, empower_science1$science_career, empower_science1$science_outsideofschool, empower_science1$science_pay, empower_science1$science_job, empower_science1$good_science, empower_science1$higherlevel_science, empower_science1$science_courses)

science_prop1 <- sum(str_count(empower_science1$science, "yes")) / (sum(str_count(empower_science1$science, "no")) + sum(str_count(empower_science1$science, "yes")))
science_prop1
```

### Grade 2

```{r}
empower_science2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "post")
empower_science2$science <- paste(empower_science2$sure_science, empower_science2$science_career, empower_science2$science_outsideofschool, empower_science2$science_pay, empower_science2$science_job, empower_science2$good_science, empower_science2$higherlevel_science, empower_science2$science_courses)

science_prop2 <- sum(str_count(empower_science2$science, "yes")) / (sum(str_count(empower_science2$science, "no")) + sum(str_count(empower_science2$science, "yes")))
science_prop2
```
### Grade 3

```{r}
empower_science3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "post")
empower_science3$science <- paste(empower_science3$sure_science, empower_science3$science_career, empower_science3$science_outsideofschool, empower_science3$science_pay, empower_science3$science_job, empower_science3$good_science, empower_science3$higherlevel_science, empower_science3$science_courses)

science_prop3 <- sum(str_count(empower_science3$science, "yes")) / (sum(str_count(empower_science3$science, "no")) + sum(str_count(empower_science3$science, "yes")))
science_prop3
```

### Grade 5 magisterio

```{r}
empower_science5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "post")
empower_science5m$science <- paste(empower_science5m$sure_science, empower_science5m$science_career, empower_science5m$science_outsideofschool, empower_science5m$science_pay, empower_science5m$science_job, empower_science5m$good_science, empower_science5m$higherlevel_science, empower_science5m$science_courses)

science_prop5m <- sum(str_count(empower_science5m$science, "yes")) / (sum(str_count(empower_science5m$science, "no")) + sum(str_count(empower_science5m$science, "yes")))
science_prop5m
```

### Grade 5 bachillerato

```{r}
empower_science5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "post")
empower_science5b$science <- paste(empower_science5b$sure_science, empower_science5b$science_career, empower_science5b$science_outsideofschool, empower_science5b$science_pay, empower_science5b$science_job, empower_science5b$good_science, empower_science5b$higherlevel_science, empower_science5b$science_courses)

science_prop5b <- sum(str_count(empower_science5b$science, "yes")) / (sum(str_count(empower_science5b$science, "no")) + sum(str_count(empower_science5b$science, "yes")))
science_prop5b
```

## POST Attitudes towards engineering

The next section finds the proportion of girls in each grade who answered positively questions that related to engineering in the post-implementation survey.

### Grade 1

```{r}
empower_egr1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "post")
empower_egr1$egr <- paste(empower_egr1$new_products, empower_egr1$engineering_everyday, empower_egr1$enjoy_building, empower_egr1$interested_machines, empower_egr1$career_design, empower_egr1$curiosity_tech, empower_egr1$future_innovation, empower_egr1$mathscience_useful, empower_egr1$success_engineering, empower_egr1$i_can_build, empower_egr1$opportunity_engineering)

egr_prop1 <- sum(str_count(empower_egr1$egr, "yes")) / (sum(str_count(empower_egr1$egr, "no")) + sum(str_count(empower_egr1$egr, "yes")))
egr_prop1
```

### Grade 2

```{r}
empower_egr2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "post")
empower_egr2$egr <- paste(empower_egr2$new_products, empower_egr2$engineering_everyday, empower_egr2$enjoy_building, empower_egr2$interested_machines, empower_egr2$career_design, empower_egr2$curiosity_tech, empower_egr2$future_innovation, empower_egr2$mathscience_useful, empower_egr2$success_engineering, empower_egr2$i_can_build, empower_egr2$opportunity_engineering)

egr_prop2 <- sum(str_count(empower_egr2$egr, "yes")) / (sum(str_count(empower_egr2$egr, "no")) + sum(str_count(empower_egr2$egr, "yes")))
egr_prop2
```

### Grade 3

```{r}
empower_egr3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "post")
empower_egr3$egr <- paste(empower_egr3$new_products, empower_egr3$engineering_everyday, empower_egr3$enjoy_building, empower_egr3$interested_machines, empower_egr3$career_design, empower_egr3$curiosity_tech, empower_egr3$future_innovation, empower_egr3$mathscience_useful, empower_egr3$success_engineering, empower_egr3$i_can_build, empower_egr3$opportunity_engineering)

egr_prop3 <- sum(str_count(empower_egr3$egr, "yes")) / (sum(str_count(empower_egr3$egr, "no")) + sum(str_count(empower_egr3$egr, "yes")))
egr_prop3
```

### Grade 5 magisterio

```{r}
empower_egr5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "post")
empower_egr5m$egr <- paste(empower_egr5m$new_products, empower_egr5m$engineering_everyday, empower_egr5m$enjoy_building, empower_egr5m$interested_machines, empower_egr5m$career_design, empower_egr5m$curiosity_tech, empower_egr5m$future_innovation, empower_egr5m$mathscience_useful, empower_egr5m$success_engineering, empower_egr5m$i_can_build, empower_egr5m$opportunity_engineering)

egr_prop5m <- sum(str_count(empower_egr5m$egr, "yes")) / (sum(str_count(empower_egr5m$egr, "no")) + sum(str_count(empower_egr5m$egr, "yes")))
egr_prop5m
```


### Grade 5 bachillerato

```{r}
empower_egr5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "post")
empower_egr5b$egr <- paste(empower_egr5b$new_products, empower_egr5b$engineering_everyday, empower_egr5b$enjoy_building, empower_egr5b$interested_machines, empower_egr5b$career_design, empower_egr5b$curiosity_tech, empower_egr5b$future_innovation, empower_egr5b$mathscience_useful, empower_egr5b$success_engineering, empower_egr5b$i_can_build, empower_egr5b$opportunity_engineering)

egr_prop5b <- sum(str_count(empower_egr5b$egr, "yes")) / (sum(str_count(empower_egr5b$egr, "no")) + sum(str_count(empower_egr5b$egr, "yes")))
egr_prop5b
```

```{r}
avg_math <- (math_prop1 + math_prop2 + math_prop3 + math_prop5m + math_prop5b)/5
avg_science <- (science_prop1 + science_prop2 + science_prop3 + science_prop5m + science_prop5b)/5
avg_egr <- (egr_prop1 + egr_prop2 + egr_prop3 + egr_prop5m + egr_prop5b)/5
```


## Attitudes towards STEM table

I put together a table with all the proportions of girls who responded positively to math, science and engineering questions, per grade.

```{r}
stem_attitudes <- data.frame("grade" = c("1", "2", "3", "5 mag", "5bach", "Average"), "math" = c(math_prop1, math_prop2, math_prop3, math_prop5m, math_prop5b, avg_math), "science" = c(science_prop1, science_prop2, science_prop3, science_prop5m, science_prop5b, avg_science), "egr" = c(egr_prop1, egr_prop2, egr_prop3, egr_prop5m, egr_prop5b, avg_egr))
```


```{r}
stem <- data.frame("grade" = c("1", "2", "3", "5 mag", "5bach", "Average"), "prop" = c(pre_math_prop1, pre_math_prop2, pre_math_prop3, pre_math_prop5m, pre_math_prop5b, avg_math_pre, pre_science_prop1, pre_science_prop2, pre_science_prop3, pre_science_prop5m, pre_science_prop5b, avg_science_pre, pre_egr_prop1, pre_egr_prop2, pre_egr_prop3, pre_egr_prop5m, pre_egr_prop5b, avg_egr_pre, math_prop1, math_prop2, math_prop3, math_prop5m, math_prop5b, avg_math, science_prop1, science_prop2, science_prop3, science_prop5m, science_prop5b, avg_science, egr_prop1, egr_prop2, egr_prop3, egr_prop5b, egr_prop5m, avg_egr), "course" = c("math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr", "math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr"), "pre_post" = c("pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post"))
stem
```

I visualized the chart in the following bar graph. 

```{r}
stem$course <- factor(stem$course, levels = c("math", "science", "egr"))
stem$pre_post <- factor(stem$pre_post, levels = c("pre", "post"))

  ggplot(data = stem, aes(x=pre_post, y=prop, fill=course)) +
    geom_bar(stat="identity", position=position_dodge()) +
    facet_grid(~ grade) +
    labs(title = "Proportion of Students Who Feel Positively About math", 
         x = "Grade",
         y = "Proportion",
         fill = "Course")
```

Then, I found the difference in proportions of girls who feel positively about STEM. 

```{r}
stem_diffprop <- data.frame("grade" = c("1", "2", "3", "5 mag", "5bach", "Average"),  "diff_prop" = c(math_prop1-pre_math_prop1, math_prop2-pre_math_prop2, math_prop3-pre_math_prop3, math_prop5m-pre_math_prop5m, math_prop5b-pre_math_prop5b, avg_math-avg_math_pre,science_prop1-pre_science_prop1, science_prop2-pre_science_prop2, science_prop3-pre_science_prop3, science_prop5m-pre_science_prop5m, science_prop5b-pre_science_prop5b, avg_science-avg_science_pre, egr_prop1-pre_egr_prop1, egr_prop2-pre_egr_prop2, egr_prop3-pre_egr_prop3, egr_prop5b-pre_egr_prop5b, egr_prop5m-pre_egr_prop5m, avg_egr-avg_egr_pre), "course" = c("math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr", "math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr"))
stem_diffprop
```

I visualized this difference in the following graph. I feel like this should be at the crux of the investigation. 

```{r}
stem_diffprop$course <- factor(stem$course, levels = c("math", "science", "egr"))

  ggplot(data = stem_diffprop, aes(x=course, y=diff_prop, fill = grade)) +
    geom_bar(stat="identity", position=position_dodge()) +
    facet_grid(~ grade) +
    labs(title = "Difference in Proportion of Students Who Feel Positively About STEM", 
         subtitle = "Before and after the course",
         x = "Grade",
         y = "Proportion",
         fill = "Course")
```

# SECTION 3: ANALYSIS BY QUESTION

## More specifically, I analyzed what I found to be the 9 most important questions in the survey.
### The following section is lengthy and repetitive, but I used it to gauge the data initially and see how the girls' answers differed by grade and age group. I don't think I will actually include the following graphs in the analysis. I could make a Shiny app for them? I don't know if I would include that in the analysis, but it could be informative/fun?
I created three visualizations for each question: 
1. Visualizes all the girls' answers together. 
2. Separates the girls' responses by age group (Younger or Older)
3. Separates the girls' responses by their grade 

## Career in math

This question asks whether the girls would like to pursue a career related to math.  

### All grades together
```{r}
empower_new$math_career <- factor(empower_new$math_career, levels = c("yes", "neutral", "no"))
empower_new$pre_or_post <- factor(empower_new$pre_or_post, levels = c("pre", "post"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = math_career), position = "fill") +
  labs(title = "Proportion of People Who Think of a Career in Math",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Would you consider a career in math?")
```

### By age group

```{r}
empower_byage$math_career <- factor(empower_byage$math_career, levels = c("yes", "neutral", "no"))
empower_byage$pre_or_post <- factor(empower_byage$pre_or_post, levels = c("pre", "post"))
empower_byage$age_groups <- factor(empower_byage$age_groups, levels = c("younger", "older"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = math_career), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Think of a Career in Math",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in math?")
```

### By grade 

```{r}
empower_new$math_career <- factor(empower_new$math_career, levels = c("yes", "neutral", "no"))
empower_new$pre_or_post <- factor(empower_new$pre_or_post, levels = c("pre", "post"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = math_career), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Think of a Career in Math",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in math?")
```

## Good at math

This question asks whether the girls believe they are good at math.

### All grades together
```{r}
empower_new$good_at_math <- factor(empower_new$good_at_math, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = good_at_math), position = "fill") +
  labs(title = "Proportion of People Who Think They Are Good at Math",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Good at math?")
```

### By age group

```{r}
empower_byage$good_at_math <- factor(empower_byage$good_at_math, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = good_at_math), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Think They are Good at Math",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Good at math?")
```

### By grade

```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = good_at_math), position = "fill") +
  facet_grid(~ grade) +
 labs(title = "Proportion of People Who Think They are Good at Math",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Good at math?")
```

## More math courses

This question asks whether the girls would like the opportunity to take more math courses. 

### All groups together
```{r}
empower_new$math_courses <- factor(empower_new$math_courses, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = math_courses), position = "fill") +
  labs(title = "Proportion of People Who Want to Take More Math Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "More math courses?")
```

### By age group

```{r}
empower_byage$math_courses <- factor(empower_byage$math_courses, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = math_courses), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Want to Take More Math Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "More math courses?")
```

### By grade
```{r}
empower_new$math_courses <- factor(empower_new$math_courses, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = math_courses), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Want to Take More Math Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "More math courses?")
```

## Science career

This question asks whether the girls would like to pursue a career related to science.  

### All groups together

```{r}
empower_new$science_career <- factor(empower_new$science_career, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_career), position = "fill") +
  labs(title = "Proportion of People Who Think of a Career in Science",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in science?")
```

### By age group
```{r}
empower_byage$science_career <- factor(empower_byage$science_career, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_career), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Think of a Career in Science",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in science?")
```

### By grade
```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_career), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Think of a Career in Science",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in science?")
```


## Good at science 

This question asks whether the girls believe they are good at science.

### All groups together

```{r}
empower_new$good_science <- factor(empower_new$science_career, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_career), position = "fill") +
  labs(title = "Proportion of People Who Think of a Career in Science",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in science?")
```

### By age group
```{r}
empower_byage$science_career <- factor(empower_byage$science_career, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_career), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Think of a Career in Science",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in science?")
```

### By grade
```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_career), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Think of a Career in Science",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Career in science?")
```


## More science courses

This question asks whether the girls would like the opportunity to take more science courses. 

### All groups together

```{r}
empower_new$science_courses <- factor(empower_new$science_courses, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_courses), position = "fill") +
  labs(title = "Proportion of People Who Want to take More Science Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "More Science Courses?")
```

### By age group
```{r}
empower_byage$science_courses <- factor(empower_byage$science_courses, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_courses), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Want to take More Science Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "More Science Courses?")
```

### By grade
```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_courses), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Want to take More Science Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "More Science Courses?")
```


## Science and math together to invent things

This question asks whether the girls agree with the statement that knowing how to use math and science together will allow them to invent useful things. 

### All groups together

```{r}
empower_new$mathscience_useful <- factor(empower_new$mathscience_useful, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = mathscience_useful), position = "fill") +
  labs(title = "Proportion of People Who Think They Can Invent",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Can invent?")
```

### By age group
```{r}
empower_byage$mathscience_useful <- factor(empower_byage$mathscience_useful, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = mathscience_useful), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Think They Can Invent",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Can invent?")
```

### By grade
```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = science_courses), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Think They Can Invent",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Can invent?")
```

## Success in engineering

This question asks whether the girls think they could succeed at an engineering-related career. 

### All groups together

```{r}
empower_new$success_engineering <- factor(empower_new$success_engineering, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = success_engineering), position = "fill") +
  labs(title = "Proportion of People Who Think They Can Succeed as Engineers",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Can succeed?")
```

### By age group
```{r}
empower_byage$success_engineering <- factor(empower_byage$success_engineering, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = success_engineering), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Think They Can Succeed as Engineers",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Can succeed?")
```

### By grade
```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = success_engineering), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Think They Can Succeed as Engineers",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "Can succeed?")
```


## Courses in engineering

This question asks whether the girls would like the opportunity to take more science courses. 

### All groups together

```{r}
empower_new$opportunity_engineering <- factor(empower_new$opportunity_engineering, levels = c("yes", "neutral", "no"))

ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = opportunity_engineering), position = "fill") +
  labs(title = "Proportion of People Who Want to Take More EGR Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "EGR courses?")
```

### By age group
```{r}
empower_byage$opportunity_engineering <- factor(empower_byage$opportunity_engineering, levels = c("yes", "neutral", "no"))

ggplot(data = empower_byage) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = opportunity_engineering), position = "fill") +
  facet_grid(~ age_groups) +
  labs(title = "Proportion of People Who Want to Take More EGR Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "EGR Courses?")
```

### By grade
```{r}
ggplot(data = empower_new) +
  geom_bar(mapping = aes(x = pre_or_post, 
                         fill = opportunity_engineering), position = "fill") +
  facet_grid(~ grade) +
  labs(title = "Proportion of People Who Want to Take More EGR Courses",
       x = "Pre or Post",
       y = "Proportions", 
       fill = "EGR Courses?")
```




## Personal Notes:

### Template for finding proportions

prop_pre_mathcareer <- empower_new %>%
  filter(!is.na(math_career)) %>%
  count(math_career, pre_or_post) %>%
  group_by(pre_or_post) %>%
  mutate(perc = (n / sum(n))*100) %>%
  select(math_career, pre_or_post, perc) %>%
  filter(pre_or_post == "pre")
prop_pre_mathcareer


### Ideas 

How predicted grades vary between subjects
