---
title: "Empowerment Survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load packages
```{r load-packages, message=FALSE}
library(tidyverse)
library(ggplot2)
library(shiny)
```

### Background Information
This survey was conducted on 143 girls in an all-female boarding school in Guatemala before and after a pair of Duke students conducted STEM-focused courses. Grade 1 would be equivalent to 7th grade in the American school system. We taught girls in grades 1, 2, and 3 the same curriculum, and girls in grades 5 magisterio (mag) and 5 bachillerato (bach) another curriculum. In 2017, the girls in 5 magisterio and 5 bachillerato took the curriculum that grades 1, 2, and 3 took in 2018. The girls in 5 magisterio are on a program specifically to become school teachers. The girls in 5 bachillerato usually pursue careers other than teaching. 

### Purpose
The purpose of the course is to give girls the chance to explore STEM-related courses and help them realize that they are capable of pursuing STEM-related careers, if they want to. 

Thus, the purpose of the survey is to evaluate the girls' attitudes towards STEM and STEM-related careers before and after the course. 

### A note for Professor Tackett
I feel like a have a lot of interesting data and visualizations, but I am unsure about what direction to take the statistical research in order to come to important conclusions about the curriculum. 

I am thinking that some of the important takeaways could be observations about how the program's effect differs: 
- Between older and younger girls (middle vs. high school)
- Between different grade levels (more specific than just saying younger vs. older)
- Between girls who are on the teaching-specific program (5 magisterio) vs. those who might have time to decide on their career path (5 bach and grades 1-3)
- Between girls who took the course last year and those who did not 

However, I am stuck on how to decide which of these paths to pursue. 

Furthermore, the lab through which I am doing this investigation failed to send me the Post-Implementation survey for 2017, so I only have the Pre-Implementation survey for 2017. The survey in 2017 was much shorter. However, we might be able to draw some comparisons between 2017 and 2018, once I get all the 2017 data. 

Finally, how do I factor in things that were not directly addressed in the survey? For example, at Flunch we talked about how the girls might have felt inclined to answer the post-implementation survey more positively because they liked their teachers, not necessarily because they liked the subject. 

### Load data
```{r load-data}
pre_empower <- read.csv("data/PRE_Empowerment.csv",
                    sep = ";")
post_empower <- read.csv("data/POST_Empowerment.csv",
                    sep = ";")
pre_empower2017 <- read.csv("data/2017_Empower.csv",
                    sep = ";")
```

# SECTION 1: ORGANIZING DATA
### Classifying and joining pre and post responses 
```{r data}
pre_empower <- pre_empower %>%
  mutate(pre_or_post = "pre") %>%
  mutate(year = "2018")
post_empower <- post_empower %>%
  mutate(pre_or_post = "post") %>%
  mutate(year = "2018")
pre_empower2017 <- pre_empower2017 %>%
  mutate(pre_or_post = "pre") %>%
  mutate(year = "2017")
```

```{r join-data}
empower <- full_join(pre_empower, post_empower)
```

### Rank
```{r id-numbers}
empower$ID <- seq.int(nrow(empower))
```

### Changing responses from letters to words and characterizing them as "Positive" or "Negative" 

To reduce the variability of the data, I joined the answers "Absolutely" with "Yes" to define someone who feels positively about a certain question. I joined "No" with "Absolutely Not" to define someone who feels negatively about a certain question. 

```{r change-names}
change_names <- function(naming){
naming %>%
  str_replace("A", "no") %>%
  str_replace("B", "no") %>%
  str_replace("C", "neutral") %>%
  str_replace("D", "yes") %>%
  str_replace("E", "yes")
}

change_names2 <- function(naming){
naming %>%
  str_replace("A", "very good") %>%
  str_replace("B", "okay") %>%
  str_replace("C", "bad")
}

change_names3 <- function(naming){
naming %>%
  str_replace("A", "yes") %>%
  str_replace("B", "no") %>%
  str_replace("C", "not sure")
}

empower$math_worst <- change_names(empower$math_worst)
empower$math_career <- change_names(empower$math_career)
empower$not_enjoy_math <- change_names(empower$not_enjoy_math)
empower$good_at_math <- change_names(empower$good_at_math)
empower$decentschool_badmath <- change_names(empower$decentschool_badmath)
empower$higherlevel_math <- change_names(empower$higherlevel_math)
empower$good_math_grades <- change_names(empower$good_math_grades)
empower$interesting_math <- change_names(empower$interesting_math)
empower$future_math <- change_names(empower$future_math)
empower$math_courses <- change_names(empower$math_courses)
empower$sure_science <- change_names(empower$sure_science)
empower$science_career <- change_names(empower$science_career)
empower$science_outsideofschool <- change_names(empower$science_outsideofschool)
empower$science_pay <- change_names(empower$science_pay)
empower$science_job <- change_names(empower$science_job)
empower$good_science <- change_names(empower$good_science)
empower$decentschool_badscience <- change_names(empower$decentschool_badscience)
empower$higherlevel_science <- change_names(empower$higherlevel_science)
empower$science_courses <- change_names(empower$science_courses)
empower$new_products <- change_names(empower$new_products)
empower$engineering_everyday <- change_names(empower$engineering_everyday)
empower$enjoy_building <- change_names(empower$enjoy_building)
empower$interested_machines <- change_names(empower$interested_machines)
empower$career_design <- change_names(empower$career_design)
empower$curiosity_tech <- change_names(empower$curiosity_tech)
empower$future_innovation <- change_names(empower$future_innovation)
empower$mathscience_useful <- change_names(empower$mathscience_useful)
empower$success_engineering <- change_names(empower$success_engineering)
empower$i_can_build <- change_names(empower$i_can_build)
empower$opportunity_engineering <- change_names(empower$opportunity_engineering)
empower$contribute_community <- change_names(empower$contribute_community)
empower$resolve_problems_community <- change_names(empower$resolve_problems_community)
empower$external_help <- change_names(empower$external_help)
empower$leader_community <- change_names(empower$leader_community)
empower$contribute_community.1 <- change_names(empower$contribute_community.1)

empower$prediction_literature <- change_names2(empower$prediction_literature)
empower$prediction_math <- change_names2(empower$prediction_math)
empower$prediction_science <- change_names2(empower$prediction_science)

empower$future_math_classes <- change_names3(empower$future_math_classes)
empower$future_science_classes <- change_names3(empower$future_science_classes)
empower$future_egr_classes <- change_names3(empower$future_egr_classes)
```

## Selecting data

I excluded variables that showed extreme variance or are not relevant to the study. For example, when they were asked whether their parents had STEM-related careers (parents_stem), many girls classified farming or other agricultural/manual labor as STEM-related careers.

I created a new data set that looks at the grades by age group ("Younger" vs. "Older")
```{r}
empower_new <- empower %>%
  select(-c(parents_stem, 
            which_parent_stem, 
            parent_profession, 
            number_science_classes, 
            number_math_classes, 
            number_tech_classes, 
            number_egr_classes))
empower_byage <- empower_new %>%
  mutate(age_groups = case_when(
    grade == "1" ~ "younger",
    grade == "2" ~ "younger",
    grade == "3" ~ "younger",
    grade == "5 bach" ~ "older",
    grade == "5 mag" ~ "older"
  ))
```

```{r}
save(empower_new, file = "data/empower_new.RData")
save(empower_byage, file = "data/empower_byage.RData")
```


# SECTION 2: PROPORTION OF GIRLS THAT RESPOND POSITIVELY TO STEM 

## PRE Attitudes towards math

This section finds the proportion of girls in each grade who answered positively questions that related to math in the pre-implementation survey.

### Grade 1 
```{r}
pre_empower_math1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "pre")
pre_empower_math1$math <- paste(pre_empower_math1$math_career, pre_empower_math1$good_at_math, pre_empower_math1$higherlevel_math, pre_empower_math1$good_math_grades, pre_empower_math1$interesting_math, pre_empower_math1$future_math, pre_empower_math1$math_courses)

pre_math_prop1 <- sum(str_count(pre_empower_math1$math, "yes")) / (sum(str_count(pre_empower_math1$math, "no")) + sum(str_count(pre_empower_math1$math, "yes")) +sum(str_count(pre_empower_math1$math, "neutral")))
pre_math_prop1
```

### Grade 2

```{r}
pre_empower_math2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "pre")
pre_empower_math2$math <- paste(pre_empower_math2$math_career, pre_empower_math2$good_at_math, pre_empower_math2$higherlevel_math, pre_empower_math2$good_math_grades, pre_empower_math2$interesting_math, pre_empower_math2$future_math, pre_empower_math2$math_courses)

pre_math_prop2 <- sum(str_count(pre_empower_math2$math, "yes")) / (sum(str_count(pre_empower_math2$math, "no")) + sum(str_count(pre_empower_math2$math, "yes")) + sum(str_count(pre_empower_math2$math, "neutral")))
pre_math_prop2
```

### Grade 3

```{r}
pre_empower_math3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "pre")
pre_empower_math3$math <- paste(pre_empower_math3$math_career, pre_empower_math3$good_at_math, pre_empower_math3$higherlevel_math, pre_empower_math3$good_math_grades, pre_empower_math3$interesting_math, pre_empower_math3$future_math, pre_empower_math3$math_courses)

pre_math_prop3 <- sum(str_count(pre_empower_math3$math, "yes")) / (sum(str_count(pre_empower_math3$math, "no")) + sum(str_count(pre_empower_math3$math, "yes")) + sum(str_count(pre_empower_math3$math, "neutral")))
pre_math_prop3
```

### Grade 5 magisterio

```{r}
pre_empower_math5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "pre")
pre_empower_math5m$math <- paste(pre_empower_math5m$math_career, pre_empower_math5m$good_at_math, pre_empower_math5m$higherlevel_math, pre_empower_math5m$good_math_grades, pre_empower_math5m$interesting_math, pre_empower_math5m$future_math, pre_empower_math5m$math_courses)

pre_math_prop5m <- sum(str_count(pre_empower_math5m$math, "yes")) / (sum(str_count(pre_empower_math5m$math, "no")) + sum(str_count(pre_empower_math5m$math, "yes")) + sum(str_count(pre_empower_math5m$math, "neutral")))
pre_math_prop5m
```

### Grade 5 bachillerato

```{r}
pre_empower_math5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "pre")
pre_empower_math5b$math <- paste(pre_empower_math5b$math_career, pre_empower_math5b$good_at_math, pre_empower_math5b$higherlevel_math, pre_empower_math5b$good_math_grades, pre_empower_math5b$interesting_math, pre_empower_math5b$future_math, pre_empower_math5b$math_courses)

pre_math_prop5b <- sum(str_count(pre_empower_math5b$math, "yes")) / (sum(str_count(pre_empower_math5b$math, "no")) + sum(str_count(pre_empower_math5b$math, "yes")) + sum(str_count(pre_empower_math5b$math, "neutral")))
pre_math_prop5b
```

## PRE Attitudes towards science

The next section finds the proportion of girls in each grade who answered positively questions that related to science in the pre-implementation survey.

### Grade 1

```{r}
pre_empower_science1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "pre")
pre_empower_science1$science <- paste(pre_empower_science1$sure_science, pre_empower_science1$science_career, pre_empower_science1$science_outsideofschool, pre_empower_science1$science_pay, pre_empower_science1$science_job, pre_empower_science1$good_science, pre_empower_science1$higherlevel_science, pre_empower_science1$science_courses)

pre_science_prop1 <- sum(str_count(pre_empower_science1$science, "yes")) / (sum(str_count(pre_empower_science1$science, "no")) + sum(str_count(pre_empower_science1$science, "yes")) + sum(str_count(pre_empower_science1$science, "neutral")))
pre_science_prop1
```

### Grade 2

```{r}
pre_empower_science2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "pre")
pre_empower_science2$science <- paste(pre_empower_science2$sure_science, pre_empower_science2$science_career, pre_empower_science2$science_outsideofschool, pre_empower_science2$science_pay, pre_empower_science2$science_job, pre_empower_science2$good_science, pre_empower_science2$higherlevel_science, pre_empower_science2$science_courses)

pre_science_prop2 <- sum(str_count(pre_empower_science2$science, "yes")) / (sum(str_count(pre_empower_science2$science, "no")) + sum(str_count(pre_empower_science2$science, "yes")) + sum(str_count(pre_empower_science2$science, "neutral")))
pre_science_prop2
```
### Grade 3

```{r}
pre_empower_science3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "pre")
pre_empower_science3$science <- paste(pre_empower_science3$sure_science, pre_empower_science3$science_career, pre_empower_science3$science_outsideofschool, pre_empower_science3$science_pay, pre_empower_science3$science_job, pre_empower_science3$good_science, pre_empower_science3$higherlevel_science, pre_empower_science3$science_courses)

pre_science_prop3 <- sum(str_count(pre_empower_science3$science, "yes")) / (sum(str_count(pre_empower_science3$science, "no")) + sum(str_count(pre_empower_science3$science, "yes")) + sum(str_count(pre_empower_science3$science, "neutral")))
pre_science_prop3
```

### Grade 5 magisterio

```{r}
pre_empower_science5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "pre")
pre_empower_science5m$science <- paste(pre_empower_science5m$sure_science, pre_empower_science5m$science_career, pre_empower_science5m$science_outsideofschool, pre_empower_science5m$science_pay, pre_empower_science5m$science_job, pre_empower_science5m$good_science, pre_empower_science5m$higherlevel_science, pre_empower_science5m$science_courses)

pre_science_prop5m <- sum(str_count(pre_empower_science5m$science, "yes")) / (sum(str_count(pre_empower_science5m$science, "no")) + sum(str_count(pre_empower_science5m$science, "yes")) +sum(str_count(pre_empower_science5m$science, "neutral")))
pre_science_prop5m
```

### Grade 5 bachillerato

```{r}
pre_empower_science5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "pre")
pre_empower_science5b$science <- paste(pre_empower_science5b$sure_science, pre_empower_science5b$science_career, pre_empower_science5b$science_outsideofschool, pre_empower_science5b$science_pay, pre_empower_science5b$science_job, pre_empower_science5b$good_science, pre_empower_science5b$higherlevel_science, pre_empower_science5b$science_courses)

pre_science_prop5b <- sum(str_count(pre_empower_science5b$science, "yes")) / (sum(str_count(pre_empower_science5b$science, "no")) + sum(str_count(pre_empower_science5b$science, "yes")) + sum(str_count(pre_empower_science5b$science, "neutral")))
pre_science_prop5b
```

## PRE Attitudes towards engineering

The next section finds the proportion of girls in each grade who answered positively questions that related to engineering in the pre-implementation survey.

### Grade 1

```{r}
pre_empower_egr1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "pre")
pre_empower_egr1$egr <- paste(pre_empower_egr1$new_products, pre_empower_egr1$engineering_everyday, pre_empower_egr1$enjoy_building, pre_empower_egr1$interested_machines, pre_empower_egr1$career_design, pre_empower_egr1$curiosity_tech, pre_empower_egr1$future_innovation, pre_empower_egr1$mathscience_useful, pre_empower_egr1$success_engineering, pre_empower_egr1$i_can_build, pre_empower_egr1$opportunity_engineering)

pre_egr_prop1 <- sum(str_count(pre_empower_egr1$egr, "yes")) / (sum(str_count(pre_empower_egr1$egr, "no")) + sum(str_count(pre_empower_egr1$egr, "yes")) + sum(str_count(pre_empower_egr1$egr, "neutral")))
pre_egr_prop1
```

### Grade 2

```{r}
pre_empower_egr2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "pre")
pre_empower_egr2$egr <- paste(pre_empower_egr2$new_products, pre_empower_egr2$engineering_everyday, pre_empower_egr2$enjoy_building, pre_empower_egr2$interested_machines, pre_empower_egr2$career_design, pre_empower_egr2$curiosity_tech, pre_empower_egr2$future_innovation, pre_empower_egr2$mathscience_useful, pre_empower_egr2$success_engineering, pre_empower_egr2$i_can_build, pre_empower_egr2$opportunity_engineering)

pre_egr_prop2 <- sum(str_count(pre_empower_egr2$egr, "yes")) / (sum(str_count(pre_empower_egr2$egr, "no")) + sum(str_count(pre_empower_egr2$egr, "yes")) + sum(str_count(pre_empower_egr2$egr, "neutral")))
pre_egr_prop2
```

### Grade 3

```{r}
pre_empower_egr3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "pre")
pre_empower_egr3$egr <- paste(pre_empower_egr3$new_products, pre_empower_egr3$engineering_everyday, pre_empower_egr3$enjoy_building, pre_empower_egr3$interested_machines, pre_empower_egr3$career_design, pre_empower_egr3$curiosity_tech, pre_empower_egr3$future_innovation, pre_empower_egr3$mathscience_useful, pre_empower_egr3$success_engineering, pre_empower_egr3$i_can_build, pre_empower_egr3$opportunity_engineering)

pre_egr_prop3 <- sum(str_count(pre_empower_egr3$egr, "yes")) / (sum(str_count(pre_empower_egr3$egr, "no")) + sum(str_count(pre_empower_egr3$egr, "yes")) + sum(str_count(pre_empower_egr3$egr, "neutral")))
pre_egr_prop3
```

### Grade 5 magisterio

```{r}
pre_empower_egr5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "pre")
pre_empower_egr5m$egr <- paste(pre_empower_egr5m$new_products, pre_empower_egr5m$engineering_everyday, pre_empower_egr5m$enjoy_building, pre_empower_egr5m$interested_machines, pre_empower_egr5m$career_design, pre_empower_egr5m$curiosity_tech, pre_empower_egr5m$future_innovation, pre_empower_egr5m$mathscience_useful, pre_empower_egr5m$success_engineering, pre_empower_egr5m$i_can_build, pre_empower_egr5m$opportunity_engineering)

pre_egr_prop5m <- sum(str_count(pre_empower_egr5m$egr, "yes")) / (sum(str_count(pre_empower_egr5m$egr, "no")) + sum(str_count(pre_empower_egr5m$egr, "yes")) +
                                                              sum(str_count(pre_empower_egr5m$egr, "yes")))
pre_egr_prop5m
```


### Grade 5 bachillerato

```{r}
pre_empower_egr5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "pre")
pre_empower_egr5b$egr <- paste(pre_empower_egr5b$new_products, pre_empower_egr5b$engineering_everyday, pre_empower_egr5b$enjoy_building, pre_empower_egr5b$interested_machines, pre_empower_egr5b$career_design, pre_empower_egr5b$curiosity_tech, pre_empower_egr5b$future_innovation, pre_empower_egr5b$mathscience_useful, pre_empower_egr5b$success_engineering, pre_empower_egr5b$i_can_build, pre_empower_egr5b$opportunity_engineering)

pre_egr_prop5b <- sum(str_count(pre_empower_egr5b$egr, "yes")) / (sum(str_count(pre_empower_egr5b$egr, "no")) + sum(str_count(pre_empower_egr5b$egr, "yes")) +
                                                                    sum(str_count(pre_empower_egr5b$egr, "yes")))
pre_egr_prop5b
```

```{r}
avg_math_pre <- (pre_math_prop1 + pre_math_prop2 + pre_math_prop3 + pre_math_prop5m + pre_math_prop5b)/5
avg_science_pre <- (pre_science_prop1 + pre_science_prop2 + pre_science_prop3 + pre_science_prop5m + pre_science_prop5b)/5
avg_egr_pre <- (pre_egr_prop1 + pre_egr_prop2 + pre_egr_prop3 + pre_egr_prop5m + pre_egr_prop5b)/5
```


## POST Attitudes towards math

The next section finds the proportion of girls in each grade who answered positively questions that related to math in the post-implementation survey.

### Grade 1 
```{r}
empower_math1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "post")
empower_math1$math <- paste(empower_math1$math_career, empower_math1$good_at_math, empower_math1$higherlevel_math, empower_math1$good_math_grades, empower_math1$interesting_math, empower_math1$future_math, empower_math1$math_courses)

math_prop1 <- sum(str_count(empower_math1$math, "yes")) / (sum(str_count(empower_math1$math, "no")) + sum(str_count(empower_math1$math, "yes")) + sum(str_count(empower_math1$math, "neutral")))
math_prop1
```

### Grade 2

```{r}
empower_math2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "post")
empower_math2$math <- paste(empower_math2$math_career, empower_math2$good_at_math, empower_math2$higherlevel_math, empower_math2$good_math_grades, empower_math2$interesting_math, empower_math2$future_math, empower_math2$math_courses)

math_prop2 <- sum(str_count(empower_math2$math, "yes")) / (sum(str_count(empower_math2$math, "no")) + sum(str_count(empower_math2$math, "yes")) + sum(str_count(empower_math2$math, "neutral")))
math_prop2
```

### Grade 3

```{r}
empower_math3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "post")
empower_math3$math <- paste(empower_math3$math_career, empower_math3$good_at_math, empower_math3$higherlevel_math, empower_math3$good_math_grades, empower_math3$interesting_math, empower_math3$future_math, empower_math3$math_courses)

math_prop3 <- sum(str_count(empower_math3$math, "yes")) / (sum(str_count(empower_math3$math, "no")) + sum(str_count(empower_math3$math, "yes")) + sum(str_count(empower_math3$math, "neutral")))
math_prop3
```

### Grade 5 magisterio

```{r}
empower_math5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "post")
empower_math5m$math <- paste(empower_math5m$math_career, empower_math5m$good_at_math, empower_math5m$higherlevel_math, empower_math5m$good_math_grades, empower_math5m$interesting_math, empower_math5m$future_math, empower_math5m$math_courses)

math_prop5m <- sum(str_count(empower_math5m$math, "yes")) / (sum(str_count(empower_math5m$math, "no")) + sum(str_count(empower_math5m$math, "yes")) + sum(str_count(empower_math5m$math, "neutral")))
math_prop5m
```

### Grade 5 bachillerato

```{r}
empower_math5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "post")
empower_math5b$math <- paste(empower_math5b$math_career, empower_math5b$good_at_math, empower_math5b$higherlevel_math, empower_math5b$good_math_grades, empower_math5b$interesting_math, empower_math5b$future_math, empower_math5b$math_courses)

math_prop5b <- sum(str_count(empower_math5b$math, "yes")) / (sum(str_count(empower_math5b$math, "no")) + sum(str_count(empower_math5b$math, "yes")) + sum(str_count(empower_math5b$math, "neutral")))
math_prop5b
```

## POST Attitudes towards science

The next section finds the proportion of girls in each grade who answered positively questions that related to science in the post-implementation survey.

### Grade 1

```{r}
empower_science1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "post")
empower_science1$science <- paste(empower_science1$sure_science, empower_science1$science_career, empower_science1$science_outsideofschool, empower_science1$science_pay, empower_science1$science_job, empower_science1$good_science, empower_science1$higherlevel_science, empower_science1$science_courses)

science_prop1 <- sum(str_count(empower_science1$science, "yes")) / (sum(str_count(empower_science1$science, "no")) + sum(str_count(empower_science1$science, "yes")) + sum(str_count(empower_science1$science, "neutral")))
science_prop1
```

### Grade 2

```{r}
empower_science2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "post")
empower_science2$science <- paste(empower_science2$sure_science, empower_science2$science_career, empower_science2$science_outsideofschool, empower_science2$science_pay, empower_science2$science_job, empower_science2$good_science, empower_science2$higherlevel_science, empower_science2$science_courses)

science_prop2 <- sum(str_count(empower_science2$science, "yes")) / (sum(str_count(empower_science2$science, "no")) + sum(str_count(empower_science2$science, "yes")) + sum(str_count(empower_science2$science, "neutral")))
science_prop2
```
### Grade 3

```{r}
empower_science3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "post")
empower_science3$science <- paste(empower_science3$sure_science, empower_science3$science_career, empower_science3$science_outsideofschool, empower_science3$science_pay, empower_science3$science_job, empower_science3$good_science, empower_science3$higherlevel_science, empower_science3$science_courses)

science_prop3 <- sum(str_count(empower_science3$science, "yes")) / (sum(str_count(empower_science3$science, "no")) + sum(str_count(empower_science3$science, "yes")) + sum(str_count(empower_science3$science, "neutral")))
science_prop3
```

### Grade 5 magisterio

```{r}
empower_science5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "post")
empower_science5m$science <- paste(empower_science5m$sure_science, empower_science5m$science_career, empower_science5m$science_outsideofschool, empower_science5m$science_pay, empower_science5m$science_job, empower_science5m$good_science, empower_science5m$higherlevel_science, empower_science5m$science_courses)

science_prop5m <- sum(str_count(empower_science5m$science, "yes")) / (sum(str_count(empower_science5m$science, "no")) + sum(str_count(empower_science5m$science, "yes")) + sum(str_count(empower_science5m$science, "neutral")))
science_prop5m
```

### Grade 5 bachillerato

```{r}
empower_science5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "post")
empower_science5b$science <- paste(empower_science5b$sure_science, empower_science5b$science_career, empower_science5b$science_outsideofschool, empower_science5b$science_pay, empower_science5b$science_job, empower_science5b$good_science, empower_science5b$higherlevel_science, empower_science5b$science_courses)

science_prop5b <- sum(str_count(empower_science5b$science, "yes")) / (sum(str_count(empower_science5b$science, "no")) + sum(str_count(empower_science5b$science, "yes")) + sum(str_count(empower_science5b$science, "neutral")))
science_prop5b
```

## POST Attitudes towards engineering

The next section finds the proportion of girls in each grade who answered positively questions that related to engineering in the post-implementation survey.

### Grade 1

```{r}
empower_egr1 <- empower_new %>%
  filter(grade == "1") %>%
  filter(pre_or_post == "post")
empower_egr1$egr <- paste(empower_egr1$new_products, empower_egr1$engineering_everyday, empower_egr1$enjoy_building, empower_egr1$interested_machines, empower_egr1$career_design, empower_egr1$curiosity_tech, empower_egr1$future_innovation, empower_egr1$mathscience_useful, empower_egr1$success_engineering, empower_egr1$i_can_build, empower_egr1$opportunity_engineering)

egr_prop1 <- sum(str_count(empower_egr1$egr, "yes")) / (sum(str_count(empower_egr1$egr, "no")) + sum(str_count(empower_egr1$egr, "yes")) + sum(str_count(empower_egr1$egr, "neutral")))
egr_prop1
```

### Grade 2

```{r}
empower_egr2 <- empower_new %>%
  filter(grade == "2") %>%
  filter(pre_or_post == "post")
empower_egr2$egr <- paste(empower_egr2$new_products, empower_egr2$engineering_everyday, empower_egr2$enjoy_building, empower_egr2$interested_machines, empower_egr2$career_design, empower_egr2$curiosity_tech, empower_egr2$future_innovation, empower_egr2$mathscience_useful, empower_egr2$success_engineering, empower_egr2$i_can_build, empower_egr2$opportunity_engineering)

egr_prop2 <- sum(str_count(empower_egr2$egr, "yes")) / (sum(str_count(empower_egr2$egr, "no")) + sum(str_count(empower_egr2$egr, "yes")) + sum(str_count(empower_egr2$egr, "neutral")))
egr_prop2
```

### Grade 3

```{r}
empower_egr3 <- empower_new %>%
  filter(grade == "3") %>%
  filter(pre_or_post == "post")
empower_egr3$egr <- paste(empower_egr3$new_products, empower_egr3$engineering_everyday, empower_egr3$enjoy_building, empower_egr3$interested_machines, empower_egr3$career_design, empower_egr3$curiosity_tech, empower_egr3$future_innovation, empower_egr3$mathscience_useful, empower_egr3$success_engineering, empower_egr3$i_can_build, empower_egr3$opportunity_engineering)

egr_prop3 <- sum(str_count(empower_egr3$egr, "yes")) / (sum(str_count(empower_egr3$egr, "no")) + sum(str_count(empower_egr3$egr, "yes")) + sum(str_count(empower_egr3$egr, "neutral")))
egr_prop3
```

### Grade 5 magisterio

```{r}
empower_egr5m <- empower_new %>%
  filter(grade == "5 mag") %>%
  filter(pre_or_post == "post")
empower_egr5m$egr <- paste(empower_egr5m$new_products, empower_egr5m$engineering_everyday, empower_egr5m$enjoy_building, empower_egr5m$interested_machines, empower_egr5m$career_design, empower_egr5m$curiosity_tech, empower_egr5m$future_innovation, empower_egr5m$mathscience_useful, empower_egr5m$success_engineering, empower_egr5m$i_can_build, empower_egr5m$opportunity_engineering)

egr_prop5m <- sum(str_count(empower_egr5m$egr, "yes")) / (sum(str_count(empower_egr5m$egr, "no")) + sum(str_count(empower_egr5m$egr, "yes")) + sum(str_count(empower_egr5m$egr, "neutral")))
egr_prop5m
```


### Grade 5 bachillerato

```{r}
empower_egr5b <- empower_new %>%
  filter(grade == "5 bach") %>%
  filter(pre_or_post == "post")
empower_egr5b$egr <- paste(empower_egr5b$new_products, empower_egr5b$engineering_everyday, empower_egr5b$enjoy_building, empower_egr5b$interested_machines, empower_egr5b$career_design, empower_egr5b$curiosity_tech, empower_egr5b$future_innovation, empower_egr5b$mathscience_useful, empower_egr5b$success_engineering, empower_egr5b$i_can_build, empower_egr5b$opportunity_engineering)

egr_prop5b <- sum(str_count(empower_egr5b$egr, "yes")) / (sum(str_count(empower_egr5b$egr, "no")) + sum(str_count(empower_egr5b$egr, "yes")) + sum(str_count(empower_egr5b$egr, "neutral")))
egr_prop5b
```

```{r}
avg_math <- (math_prop1 + math_prop2 + math_prop3 + math_prop5m + math_prop5b)/5
avg_science <- (science_prop1 + science_prop2 + science_prop3 + science_prop5m + science_prop5b)/5
avg_egr <- (egr_prop1 + egr_prop2 + egr_prop3 + egr_prop5m + egr_prop5b)/5
```


## Attitudes towards STEM table

I put together a table with all the proportions of girls who responded positively to math, science and engineering questions, per grade.

```{r}
stem_attitudes <- data.frame("grade" = c("1", "2", "3", "5 mag", "5bach", "Average"), "math" = c(math_prop1, math_prop2, math_prop3, math_prop5m, math_prop5b, avg_math), "science" = c(science_prop1, science_prop2, science_prop3, science_prop5m, science_prop5b, avg_science), "egr" = c(egr_prop1, egr_prop2, egr_prop3, egr_prop5m, egr_prop5b, avg_egr))
```


```{r}
stem <- data.frame("grade" = c("1", "2", "3", "5 mag", "5bach", "Average"), "prop" = c(pre_math_prop1, pre_math_prop2, pre_math_prop3, pre_math_prop5m, pre_math_prop5b, avg_math_pre, pre_science_prop1, pre_science_prop2, pre_science_prop3, pre_science_prop5m, pre_science_prop5b, avg_science_pre, pre_egr_prop1, pre_egr_prop2, pre_egr_prop3, pre_egr_prop5m, pre_egr_prop5b, avg_egr_pre, math_prop1, math_prop2, math_prop3, math_prop5m, math_prop5b, avg_math, science_prop1, science_prop2, science_prop3, science_prop5m, science_prop5b, avg_science, egr_prop1, egr_prop2, egr_prop3, egr_prop5b, egr_prop5m, avg_egr), "course" = c("math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr", "math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr"), "pre_post" = c("pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "pre", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post", "post"))
stem
```

I visualized the chart in the following bar graph. 

```{r}
stem$course <- factor(stem$course, levels = c("math", "science", "egr"))
stem$pre_post <- factor(stem$pre_post, levels = c("pre", "post"))

  ggplot(data = stem, aes(x=pre_post, y=prop, fill=course)) +
    geom_bar(stat="identity", position=position_dodge()) +
    facet_grid(~ grade) +
    labs(title = "Proportion of Students Who Feel Positively About STEM", 
         x = "Grade",
         y = "Proportion",
         fill = "Course")
```

Then, I found the difference in proportions of girls who feel positively about STEM. 

```{r}
stem_diffprop <- data.frame("grade" = c("1", "2", "3", "5 mag", "5bach", "Average"),  "diff_prop" = c(math_prop1-pre_math_prop1, math_prop2-pre_math_prop2, math_prop3-pre_math_prop3, math_prop5m-pre_math_prop5m, math_prop5b-pre_math_prop5b, avg_math-avg_math_pre,science_prop1-pre_science_prop1, science_prop2-pre_science_prop2, science_prop3-pre_science_prop3, science_prop5m-pre_science_prop5m, science_prop5b-pre_science_prop5b, avg_science-avg_science_pre, egr_prop1-pre_egr_prop1, egr_prop2-pre_egr_prop2, egr_prop3-pre_egr_prop3, egr_prop5b-pre_egr_prop5b, egr_prop5m-pre_egr_prop5m, avg_egr-avg_egr_pre), "course" = c("math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr", "math", "math", "math", "math", "math", "math", "science", "science", "science", "science", "science", "science", "egr", "egr", "egr", "egr", "egr", "egr"))
stem_diffprop
```

I visualized this difference in the following graph. I feel like this should be at the crux of the investigation. 

```{r}
stem_diffprop$course <- factor(stem$course, levels = c("math", "science", "egr"))

  ggplot(data = stem_diffprop, aes(x=course, y=diff_prop, fill = grade)) +
    geom_bar(stat="identity", position=position_dodge()) +
    facet_grid(~ grade) +
    labs(title = "Difference in Proportion of Students Who Feel Positively About STEM", 
         subtitle = "Before and after the course",
         x = "Grade",
         y = "Proportion",
         fill = "Course")
```

# SECTION 3: ANALYSIS BY QUESTION

## More specifically, I analyzed what I found to be the 9 most important questions in the survey.
### The graphs are repetitive, so I created a ShinyApp to keep them more organized. I don't think I will actually include the following graphs in the analysis, but I used it to gauge the data initially and see how the girls' answers differed by grade and age group. 
I created three visualizations for each question: 
1. Visualizes all the girls' answers together. 
2. Separates the girls' responses by age group (Younger or Older)
3. Separates the girls' responses by their grade 

The following are the number of girls in each of the groups outlined above. 

All the girls:
```{r}
empower_new %>%
  count()
```

By age group:
```{r}
empower_byage %>%
  count(age_groups)
```

By grade:
```{r}
empower_new %>%
  count(grade)
```





# Pre 2017 vs. Pre 2018 Analysis

## Renaming the 2017 answers
```{r rename}
change_names <- function(naming){
naming %>%
  str_replace("1", "no") %>%
  str_replace("2", "no") %>%
  str_replace("3", "neutral") %>%
  str_replace("4", "yes") %>%
  str_replace("5", "yes")
}

pre_empower2017$understanding_stem <- change_names(pre_empower2017$understanding_stem)
pre_empower2017$enjoy_stem <- change_names(pre_empower2017$enjoy_stem)
pre_empower2017$interest_stem_classes <- change_names(pre_empower2017$interest_stem_classes)
pre_empower2017$interest_stem_career <- change_names(pre_empower2017$interest_stem_career)
```

### Finding proportions of positive answers for each question 2017
```{r}
understanding <- pre_empower2017 %>%
  filter(!is.na(understanding_stem)) 

understanding <- sum(str_count(understanding$understanding_stem, "yes")) / (sum(str_count(understanding$understanding_stem, "no")) + sum(str_count(understanding$understanding_stem, "yes")) + sum(str_count(understanding$understanding_stem, "neutral")))
understanding
```

```{r}
enjoy <- pre_empower2017 %>%
  filter(!is.na(enjoy_stem)) 

enjoy <- sum(str_count(enjoy$enjoy_stem, "yes")) / (sum(str_count(enjoy$enjoy_stem, "no")) + sum(str_count(enjoy$enjoy_stem, "yes")) + sum(str_count(enjoy$enjoy_stem, "neutral")))
enjoy
```

```{r}
interest_classes <- pre_empower2017 %>%
  filter(!is.na(interest_stem_classes)) 

interest_classes <- sum(str_count(interest_classes$interest_stem_classes, "yes")) / (sum(str_count(interest_classes$interest_stem_classes, "no")) + sum(str_count(interest_classes$interest_stem_classes, "yes")) + sum(str_count(interest_classes$interest_stem_classes, "neutral")))
interest_classes
```

```{r}
interest_career <- pre_empower2017 %>%
  filter(!is.na(interest_stem_classes)) 

interest_career <- sum(str_count(interest_career$interest_stem_classes, "yes")) / (sum(str_count(interest_career$interest_stem_classes, "no")) + sum(str_count(interest_career$interest_stem_classes, "yes")) + sum(str_count(interest_career$interest_stem_classes, "neutral")))
interest_career
```


## Joining answers by same categories as 2017 in the 2018 data and finding proportions of positive answers
```{r}
pre <- empower_new %>%
  filter(pre_or_post == "pre")
pre$careers <- paste(pre$math_career, pre$science_career, pre$future_innovation)

pre_careers_prop <- sum(str_count(pre$careers, "yes")) / (sum(str_count(pre$careers, "no")) + sum(str_count(pre$careers, "yes")) + sum(str_count(pre$careers, "neutral")))
pre_careers_prop
```

```{r}
pre$understanding <- paste(pre$good_at_math, pre$good_science, pre$i_can_build)

pre_understanding_prop <- sum(str_count(pre$understanding, "yes")) / (sum(str_count(pre$understanding, "no")) + sum(str_count(pre$understanding, "yes")) + sum(str_count(pre$understanding, "neutral")))
pre_understanding_prop
```

```{r}
pre$enjoy <- paste(pre$higherlevel_math, pre$higherlevel_science, pre$enjoy_building)

pre_enjoy_prop <- sum(str_count(pre$enjoy, "yes")) / (sum(str_count(pre$enjoy, "no")) + sum(str_count(pre$enjoy, "yes")) + sum(str_count(pre$enjoy, "neutral")))
pre_enjoy_prop
```

```{r}
pre$classes <- paste(pre$math_courses, pre$science_courses, pre$opportunity_engineering)

pre_classes_prop <- sum(str_count(pre$classes, "yes")) / (sum(str_count(pre$classes, "no")) + sum(str_count(pre$classes, "yes")) + sum(str_count(pre$classes, "neutral")))
pre_classes_prop
```


```{r}
years_comparison <- data.frame("category" = c("understanding STEM", "enjoy STEM", "STEM classes", "STEM career"), "prop" = c(understanding, enjoy, interest_classes, interest_career, pre_understanding_prop, pre_enjoy_prop, pre_classes_prop, pre_careers_prop), "year" = c("2017", "2017", "2017", "2017", "2018", "2018", "2018", "2018"))
```


```{r}
ggplot(data = years_comparison, aes(x=year, y=prop, fill=category)) +
    geom_bar(stat="identity", position=position_dodge()) +
    facet_grid(~ category) +
    labs(title = "Proportion of Students Who Feel Positively About STEM", 
         x = "Year",
         y = "Proportion",
         fill = "Question")
```


## Personal Notes:

### Template for finding proportions

prop_pre_mathcareer <- empower_new %>%
  filter(!is.na(math_career)) %>%
  count(math_career, pre_or_post) %>%
  group_by(pre_or_post) %>%
  mutate(perc = (n / sum(n))*100) %>%
  select(math_career, pre_or_post, perc) %>%
  filter(pre_or_post == "pre")
prop_pre_mathcareer


### Ideas 

How predicted grades vary between subjects
