---
title: "Simulations"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r load-packages, message=FALSE}
library(tidyverse)
library(ggplot2)
library(shiny)
library(infer)
```

# Load data
```{r load-data}
pre_empower <- read.csv("data/PRE_Empowerment.csv",
                    sep = ";")
post_empower <- read.csv("data/POST_Empowerment.csv",
                    sep = ";")
pre_2019 <- read.csv("data/PRE2019.csv",
                    sep = ";")
post_2019 <- read.csv("data/POST2019.csv",
                    sep = ";")
```

## Include columns that indicate whether responses are from pre- or post-implementation surveys, and what year they were collected
```{r data}
pre_empower <- pre_empower %>%
  mutate(pre_or_post = "Pre") %>%
  mutate(year = "2018")
post_empower <- post_empower %>%
  mutate(pre_or_post = "Post") %>%
  mutate(year = "2018")
pre_2019 <- pre_2019 %>%
  mutate(pre_or_post = "Pre") %>%
  mutate(year = "2019")
post_2019 <- post_2019 %>%
  mutate(pre_or_post = "Post") %>%
  mutate(year = "2019")
```

## Count how many students took the pre- and post-implementation surveys in 2018 and 2019
```{r}
count(pre_empower)
count(post_empower)
count(pre_2019)
count(post_2019)
```

## Join pre- and post-implementation data into one dataset. Then join data from 2018 and 2019 into one dataset
```{r}
empower_2018 <- full_join(pre_empower, post_empower) %>%
  select(-c(other_plan_afterschool))
empower_2019 <- full_join(pre_2019, post_2019) %>%
  select(-c(other_plan_afterschool))
empower_2019$grade <- as.factor(empower_2019$grade)
empower <- full_join(empower_2018, empower_2019)
```

## Rename to positive vs. negative feelings from A, B, C, D, E (as they were on the survey) to 1, 2, 3, 4, 5
```{r change-names}
change_names <- function(naming){
naming %>%
  str_replace("A", "1") %>%
  str_replace("B", "2") %>%
  str_replace("C", "3") %>%
  str_replace("D", "4") %>%
  str_replace("E", "5")
}

empower$math_worst <- change_names(empower$math_worst)
empower$math_career <- change_names(empower$math_career)
empower$not_enjoy_math <- change_names(empower$not_enjoy_math)
empower$good_at_math <- change_names(empower$good_at_math)
empower$decentschool_badmath <- change_names(empower$decentschool_badmath)
empower$higherlevel_math <- change_names(empower$higherlevel_math)
empower$good_math_grades <- change_names(empower$good_math_grades)
empower$interesting_math <- change_names(empower$interesting_math)
empower$future_math <- change_names(empower$future_math)
empower$math_courses <- change_names(empower$math_courses)
empower$sure_science <- change_names(empower$sure_science)
empower$science_career <- change_names(empower$science_career)
empower$science_outsideofschool <- change_names(empower$science_outsideofschool)
empower$science_pay <- change_names(empower$science_pay)
empower$science_job <- change_names(empower$science_job)
empower$good_science <- change_names(empower$good_science)
empower$decentschool_badscience <- change_names(empower$decentschool_badscience)
empower$higherlevel_science <- change_names(empower$higherlevel_science)
empower$science_courses <- change_names(empower$science_courses)
empower$new_products <- change_names(empower$new_products)
empower$engineering_everyday <- change_names(empower$engineering_everyday)
empower$enjoy_building <- change_names(empower$enjoy_building)
empower$interested_machines <- change_names(empower$interested_machines)
empower$career_design <- change_names(empower$career_design)
empower$curiosity_tech <- change_names(empower$curiosity_tech)
empower$future_innovation <- change_names(empower$future_innovation)
empower$mathscience_useful <- change_names(empower$mathscience_useful)
empower$success_engineering <- change_names(empower$success_engineering)
empower$i_can_build <- change_names(empower$i_can_build)
empower$opportunity_engineering <- change_names(empower$opportunity_engineering)
```

## Create different datasets for each question that will be analyzed. Each dataset should have the variables: "pre_or_post", "all" (the response - whether students feel positively or negatively towards the question), "grade" (the respondent's grade level), and "class" (which classifies which course the question refers to - EGR, math, or science)

### EGR
```{r}
new_products <- empower %>%
  select(pre_or_post, new_products, grade) %>%
  mutate(class = "Engineering and Technology")
names(new_products) <- c("pre_or_post", "all", "grade", "class")

engineering_everyday <- empower %>%
  select(pre_or_post, engineering_everyday, grade) %>%
  mutate(class = "Engineering and Technology")
names(engineering_everyday) <- c("pre_or_post", "all", "grade", "class")

enjoy_building <- empower %>%
  select(pre_or_post, enjoy_building, grade) %>%
  mutate(class = "Engineering and Technology")
names(enjoy_building) <- c("pre_or_post", "all", "grade", "class")

interested_machines <- empower %>%
  select(pre_or_post, interested_machines, grade) %>%
  mutate(class = "Engineering and Technology")
names(interested_machines) <- c("pre_or_post", "all", "grade", "class")

career_design <- empower %>%
  select(pre_or_post, career_design, grade) %>%
  mutate(class = "Engineering and Technology")
names(career_design) <- c("pre_or_post", "all", "grade", "class")

curiosity_tech <- empower %>%
  select(pre_or_post, curiosity_tech, grade) %>%
  mutate(class = "Engineering and Technology")
names(curiosity_tech) <- c("pre_or_post", "all", "grade", "class")

future_innovation <- empower %>%
  select(pre_or_post, future_innovation, grade) %>%
  mutate(class = "Engineering and Technology")
names(future_innovation) <- c("pre_or_post", "all", "grade", "class")

mathscience_useful <- empower %>%
  select(pre_or_post, mathscience_useful, grade) %>%
  mutate(class = "Engineering and Technology")
names(mathscience_useful) <- c("pre_or_post", "all", "grade", "class")

success_engineering <- empower %>%
  select(pre_or_post, success_engineering, grade) %>%
  mutate(class = "Engineering and Technology")
names(success_engineering) <- c("pre_or_post", "all", "grade", "class")

i_can_build <- empower %>%
  select(pre_or_post, i_can_build, grade) %>%
  mutate(class = "Engineering and Technology")
names(i_can_build) <- c("pre_or_post", "all", "grade", "class")

opportunity_engineering <- empower %>%
  select(pre_or_post, opportunity_engineering, grade) %>%
  mutate(class = "Engineering and Technology")
names(opportunity_engineering) <- c("pre_or_post", "all", "grade", "class")
```

### Science
```{r}
sure_science <- empower %>%
  select(pre_or_post, sure_science, grade) %>%
  mutate(class = "Science")
names(sure_science) <- c("pre_or_post", "all", "grade", "class")

science_career <- empower %>%
  select(pre_or_post, science_career, grade) %>%
  mutate(class = "Science")
names(science_career) <- c("pre_or_post", "all", "grade", "class")

science_outsideofschool <- empower %>%
  select(pre_or_post, science_outsideofschool, grade) %>%
  mutate(class = "Science")
names(science_outsideofschool) <- c("pre_or_post", "all", "grade", "class")

science_pay <- empower %>%
  select(pre_or_post, science_pay, grade) %>%
  mutate(class = "Science")
names(science_pay) <- c("pre_or_post", "all", "grade", "class")

science_job <- empower %>%
  select(pre_or_post, science_job, grade) %>%
  mutate(class = "Science")
names(science_job) <- c("pre_or_post", "all", "grade", "class")

good_science <- empower %>%
  select(pre_or_post, good_science, grade) %>%
  mutate(class = "Science")
names(good_science) <- c("pre_or_post", "all", "grade", "class")

higherlevel_science <- empower %>%
  select(pre_or_post, higherlevel_science, grade) %>%
  mutate(class = "Science")
names(higherlevel_science) <- c("pre_or_post", "all", "grade", "class")

science_courses <- empower %>%
  select(pre_or_post, science_courses, grade) %>%
  mutate(class = "Science")
names(science_courses) <- c("pre_or_post", "all", "grade", "class")
```


### Math
```{r}
math_career <- empower %>%
  select(pre_or_post, math_career, grade) %>%
  mutate(class = "Math")
names(math_career) <- c("pre_or_post", "all", "grade", "class")

good_at_math <- empower %>%
  select(pre_or_post, good_at_math, grade) %>%
  mutate(class = "Math")
names(good_at_math) <- c("pre_or_post", "all", "grade", "class")

higherlevel_math <- empower %>%
  select(pre_or_post, higherlevel_math, grade) %>%
  mutate(class = "Math")
names(higherlevel_math) <- c("pre_or_post", "all", "grade", "class")

good_math_grades <- empower %>%
  select(pre_or_post, good_math_grades, grade) %>%
  mutate(class = "Math")
names(good_math_grades) <- c("pre_or_post", "all", "grade", "class")

interesting_math <- empower %>%
  select(pre_or_post, interesting_math, grade) %>%
  mutate(class = "Math")
names(interesting_math) <- c("pre_or_post", "all", "grade", "class")

future_math <- empower %>%
  select(pre_or_post, future_math, grade) %>%
  mutate(class = "Math")
names(future_math) <- c("pre_or_post", "all", "grade", "class")

math_courses <- empower %>%
  select(pre_or_post, math_courses, grade) %>%
  mutate(class = "Math")
names(math_courses) <- c("pre_or_post", "all", "grade", "class")
```


## Binding all the variables to one data set, in order to conduct simulations
```{r}
together <- rbind(new_products,
             engineering_everyday,
             enjoy_building,
             interested_machines,
             career_design,
             curiosity_tech,
             future_innovation,
             mathscience_useful,
             success_engineering,
             i_can_build,
             opportunity_engineering, 
             sure_science,
             science_career, 
             science_outsideofschool,
             science_pay,
             science_job,
             good_science,
             higherlevel_science,
             science_courses,
             math_career,
             good_at_math,
             higherlevel_math,
             good_math_grades,
             interesting_math,
             future_math,
             math_courses)
```

```{r}
together <- transform(together, all = as.numeric(all))
```

```{r}
together$grade <- together$grade %>%
  str_replace("5 bach", "5") %>%
  str_replace("5 mag", "5")
together
```


## difference in mean scores pre and post ignite

```{r}
all_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) 
all_mean
```

```{r}
set.seed(2019)
perm_all <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_all %>%
  filter(stat <= all_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

```{r}
set.seed(2019)
bootstrap <- together %>%
   filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", 
            order = c("Post", "Pre"))
```

```{r}
bootstrap %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## grade 1 difference in mean scores pre and post ignite

```{r}
grade1_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean) %>%
  pull()
grade1_mean
```

## grade 1 permute

```{r}
set.seed(2019)
perm_g1 <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_g1 %>%
  filter(stat <= grade1_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

## grade 2 difference in mean scores pre and post ignite

```{r}
grade2_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean) %>%
   pull()
grade2_mean
```

```{r}
set.seed(2019)
perm_g2 <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_g2 %>%
  filter(stat <= grade2_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

## grade 3 difference in mean scores pre and post ignite

```{r}
grade3_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean)%>%
   pull()
grade3_mean
```

```{r}
set.seed(2019)
perm_g3 <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_g3 %>%
  filter(stat <= grade3_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

## grade 5 difference in mean scores pre and post ignite

```{r}
grade5_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean)%>%
   pull()
grade5_mean
```

```{r}
set.seed(2019)
perm_g5 <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_g5 %>%
  filter(stat <= grade5_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

```{r}
set.seed(2019)
bootstrap_g5 <- together %>%
   filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", 
            order = c("Post", "Pre"))
```

```{r}
bootstrap_g5 %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```

## math difference in mean scores pre and post ignite

```{r}
math_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(class == "Math") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean)%>%
   pull()
math_mean
```

```{r}
set.seed(2019)
perm_math <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(class == "Math") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_math %>%
  filter(stat <= math_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

## science difference in mean scores pre and post ignite

```{r}
science_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(class == "Science") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean)%>%
   pull()
science_mean
```

```{r}
set.seed(2019)
perm_science <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(class == "Science") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_science %>%
  filter(stat <= science_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

## egr difference in mean scores pre and post ignite

```{r}
egr_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(class == "Engineering and Technology") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(-pre_or_post, -mean)%>%
   pull()
egr_mean
```

```{r}
set.seed(2019)
perm_egr <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(class == "Engineering and Technology") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Post", "Pre"))
```

```{r}
perm_egr %>%
  filter(stat <= egr_mean) %>%
  summarise((p_value = n()/1000) * 2)
```

```{r}
set.seed(2019)
bootstrap <- together %>%
   filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
    filter(class == "Engineering and Technology") %>%
  specify(response = all, explanatory = pre_or_post) %>%
  generate(1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", 
            order = c("Post", "Pre"))
```

```{r}
bootstrap %>%
  summarize(lower_bound = quantile(stat, 0.025),
            upper_bound = quantile(stat, 0.975))
```


```{r}
difference <- c((math_mean*-1),(science_mean*-1),(egr_mean*-1))
subject <- c("Math","Science","Engineering and Technology")
subject <- factor(subject, levels = c("Math","Science","Engineering and Technology"))
pvalue <- c("P-value = 0.306", "P-value = 0.428", "P-value ~ 0")
by_subject <- data.frame(subject, difference, pvalue) 
by_subject
```

```{r}
tiff("numbers_subjects.tiff", units="in", width=8, height=6, res=300)
ggplot(data = by_subject, mapping = aes(x = subject, y = difference)) +
  geom_bar(stat = "identity", fill = "skyblue4") +
  labs(title = "Difference in Mean Scores on Attitudes Towards STEM, by Topic", subtitle = "Before and After the Implementation of Ignite", x = "Topic", y = "Mean Difference") +
  stat_identity(geom="text", position = "dodge", aes(x=subject, label=pvalue), vjust=-0.5) +
  theme(plot.title = element_text(size = 16),
  plot.subtitle = element_text(size = 14),
  axis.text=element_text(size=12),
  axis.title=element_text(size=14),
  legend.text=element_text(size=12))
dev.off()
```

```{r}
difference <- c((grade1_mean*-1),(grade2_mean*-1),(grade3_mean*-1), (grade5_mean*-1))
grade <- c("7th Grade","8th Grade ","9th Grade", "11th Grade")
grade <- factor(grade, levels = c("7th Grade","8th Grade ","9th Grade", "11th Grade"))
pvalue <- c("P-value = 0.742", "P-value = 0.764", "P-value = 0.456", "P-value ~ 0")
by_grade <- data.frame(grade, difference, pvalue) 
by_grade
```

```{r}
tiff("numbers_grades.tiff", units="in", width=8, height=6, res=300)
ggplot(data = by_grade, mapping = aes(x = grade, y = difference)) +
  geom_bar(stat = "identity", fill = "skyblue4") +
  labs(title = "Difference in Mean Scores on Attitudes Towards STEM, by Grade Level", subtitle = "Before and After the Implementation of Ignite", x = "Grade Level", y = "Mean Difference") +
  stat_identity(geom="text", position = "dodge", aes(x=grade, label=pvalue), vjust=-0.5) +
  theme(plot.title = element_text(size = 16),
  plot.subtitle = element_text(size = 14),
  axis.text=element_text(size=12),
  axis.title=element_text(size=14),
  legend.text=element_text(size=12))
dev.off()
```






```{r}
g1_pre_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Pre") %>%
  select(mean) %>%
  pull()
g1_pre_mean
```

```{r}
g1_post_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "1") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(mean) %>%
  pull()
g1_post_mean
```


```{r}
g2_pre_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Pre") %>%
  select(mean) %>%
  pull()
g2_pre_mean
```

```{r}
g2_post_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "2") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(mean) %>%
  pull()
g2_post_mean
```

```{r}
g3_pre_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Pre") %>%
  select(mean) %>%
  pull()
g3_pre_mean
```

```{r}
g3_post_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "3") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(mean) %>%
  pull()
g3_post_mean
```

```{r}
g5_pre_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Pre") %>%
  select(mean) %>%
  pull()
g5_pre_mean
```

```{r}
g5_post_mean <- together %>%
  filter(!is.na(all)) %>%
  filter(!is.na(pre_or_post)) %>%
  filter(grade == "5") %>%
  group_by(pre_or_post) %>%
  summarize(mean = mean(all)) %>%
  mutate(diff(mean)) %>%
  filter(pre_or_post == "Post") %>%
  select(mean) %>%
  pull()
g5_post_mean
```

```{r}
mean <- c((g1_pre_mean),(g2_pre_mean), (g3_pre_mean), (g5_pre_mean), (g1_post_mean), (g2_post_mean),(g3_post_mean), (g5_post_mean))
pre_post <- c(("pre"), ("pre"), ("pre"), ("pre"), ("post"), ("post"), ("post"), ("post"))
grade <- c("7th grade","8th grade","9th Grade", "11th grade")
grade <- factor(grade, levels = c("7th grade","8th grade","9th Grade", "11th grade"))
grade_means <- data.frame(grade, mean, pre_post) 
grade_means
```

```{r}
tiff("before_after.tiff", units="in", width=8, height=6, res=300)
ggplot(data = grade_means, mapping = aes(x=grade, y = mean, fill = pre_post)) +
  geom_bar(position ="dodge", stat = "identity") +
  labs(title = "Difference in Mean Scores on Attitudes Towards STEM, by Subject", subtitle = "Before and After the Implementation of Ignite", x = "Pre- or Post-Implementation", y = "Proportion") +
  theme(plot.title = element_text(size = 16),
  plot.subtitle = element_text(size = 14),
  axis.text=element_text(size=12),
  axis.title=element_text(size=14),
  legend.text=element_text(size=12))
dev.off()
```



```{r}
number_classes <- empower %>%
  select(number_math_classes, number_science_classes, number_egr_classes, number_tech_classes) 
number_classes
```


Number of classes 
```{r}
math <- number_classes %>%
  filter(!is.na(number_math_classes)) %>%
  filter(!is.na(number_science_classes)) %>%
  filter(!is.na(number_egr_classes)) %>%
  filter(!is.na(number_tech_classes)) %>%
  summarize(mean = mean(number_math_classes)) 
math
```

```{r}
science <- number_classes %>%
  filter(!is.na(number_math_classes)) %>%
  filter(!is.na(number_science_classes)) %>%
  filter(!is.na(number_egr_classes)) %>%
  summarize(mean = mean(number_science_classes)) 
science
```

```{r}
egr <- number_classes %>%
  filter(!is.na(number_math_classes)) %>%
  filter(!is.na(number_science_classes)) %>%
  filter(!is.na(number_egr_classes)) %>%
  summarize(mean = mean(number_egr_classes)) 
egr
```

```{r}
tech <- number_classes %>%
  filter(!is.na(number_math_classes)) %>%
  filter(!is.na(number_science_classes)) %>%
  filter(!is.na(number_tech_classes)) %>%
  summarize(mean = mean(number_tech_classes)) 
tech
```
